\begin{rSection}{Selected Publications}

\textbf{Books / Book Chapters}
\begin{itemize}[font=\normalfont]
\item{
    \textbf{Bei Yu} and David Z. Pan,
    ``Design for Manufacturability with Advanced Lithography'',
    Springer. (to appear)
}
\item{
    \textbf{Bei Yu} and David Z. Pan,
    ``Layout Decomposition for Triple Patterning'',
    in Encyclopedia of Algorithms, M.-Y. Kao eds., Springer.
}
\end{itemize}


\textbf{Selected Journal Papers}
\begin{itemize}[font=\normalfont]
%{{{
\item{
  \textbf{Bei Yu}, Xiaoqing Xu, Jhih-Rong Gao, Yibo Lin, Zhuo Li, Charles Alpert and David Z. Pan,
  ``Methodology for Standard Cell Compliance and Detailed Placement for Triple Patterning Lithography'',
  IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), vol.34, no.5, pp.726-739, 2015.
}
\item{
  \textbf{Bei Yu}, Kun Yuan, Duo Ding and David Z. Pan,
  ``Layout Decomposition for Triple Patterning Lithography'',
  IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), vol.34, no.3, pp.433-446, 2015.
}
\item{
  \textbf{Bei Yu}, Jhih-Rong Gao, Duo Ding, Xuan Zeng and David Z. Pan,
  ``Accurate Lithography Hotspot Detection based on PCA-SVM Classifier with Hierarchical Data Clustering'',
  Journal of Micro/Nanolithography, MEMS, and MOEMS (JM3), vol.14, no.1, 011003, 2015.
}
\item{
  \textbf{Bei Yu}, Subhendu Roy, Jhih-Rong Gao and David Z. Pan,
  ``Triple-patterning lithography (TPL) layout decomposition using end-cutting'',
  Journal of Micro/Nanolithography, MEMS, and MOEMS (JM3), vol.14, no.1, 011002, 2015.
}
\item{
  David Z. Pan, \textbf{Bei Yu} and Jhih-Rong Gao,
  ``Design for Manufacturing with Emerging Nanolithography'', 
  IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), vol.32, no.10, pp.1453-1472, 2013.
  (\textbf{Keynote Paper})
}
%}}}
\end{itemize}

\textbf{Selected Conference Papers}
\begin{itemize}[font=\normalfont]
\item{
    \textbf{Bei Yu}, David Z. Pan, Tetsuaki Matsunawa and Xuan Zeng,
    ``Machine Learning and Pattern Matching in Physical Design'',
    IEEE/ACM Asian and South Pacific Design Automation Conference (ASPDAC), pp.286--293, Japan, Jan.~19--22, 2015.
    (\textbf{Invited Paper})
}
\item{
    \textbf{Bei Yu}, Xiaoqing Xu, Jhih-Rong Gao and David Z. Pan,
    ``Methodology for Standard Cell Compliance and Detailed Placement for Triple Patterning Lithography'',
    IEEE/ACM International Conference on Computer-Aided Design (ICCAD), pp.349--356, San Jose, CA, Nov.~18--21, 2013.
    (\textbf{William J. McCalla Best Paper Award})
}
\item{
    \textbf{Bei Yu}, Jhih-Rong Gao and David Z. Pan,
    ``L-Shape based Layout Fracturing for E-Beam Lithography'',
    IEEE/ACM Asia and South Pacific Design Automation Conference (ASPDAC), pp.249--254, Japan, Jan.~22--25, 2013.
    (\textbf{Best Paper Award Nomination})
}
\item{
    Duo Ding, \textbf{Bei Yu}, Joydeep Ghosh and David Z. Pan,
	``EPIC: Efficient Prediction of IC Manufacturing Hotspots With A Unified Meta-Classification Formulatio'',
	IEEE/ACM Asia and South Pacific Design Automation Conference (ASPDAC), pp.263--270, Sydney, Australia, Jan.~30--Feb.~3, 2012.
	(\textbf{Best Paper Award})
}
\item{
    \textbf{Bei Yu}, Kun Yuan, Boyang Zhang, Duo Ding, David Z. Pan,
    ``Triple Patterning Lithography Layout Decomposition'',
    IEEE/ACM International Conference on Computer-Aided Design (ICCAD), pp.1--8, San Jose, CA, Nov.~2011.
    (\textbf{William J. McCalla Best Paper Award Nomination})
}
\end{itemize}


\end{rSection}

