\begin{rSection}{Publications}

\textbf{Journal Papers}
\begin{description}[font=\normalfont]
%{{{
\item[{[J3]}]{
        \textbf{Yibo Lin}, Bei Yu and David Z. Pan, 
    ``High Performance Dummy Fill Insertion with Coupling and Uniformity Constraints'', 
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), 2016.
    (submitted)
}
\item[{[J2]}]{
        Bei Yu, Xiaoqing Xu, Subhendu Roy, \textbf{Yibo Lin}, Jiaojiao Ou, and David Z. Pan, 
        ``\href{http://link.springer.com/article/10.1007%2Fs11432-016-5560-6}{Design for Manufacturability and Reliability in Extreme-Scaling VLSI}'', 
        Science China Information Sciences, 2016 
        (\textbf{Invited paper})
}
\item[{[J1]}]{
        Bei Yu, Xiaoqing Xu, Jhih-Rong Gao, \textbf{Yibo Lin}, Zhuo Li, Charles Alpert, and David Z. Pan, 
        ``\href{http://ieeexplore.ieee.org/xpl/articleDetails.jsp?tp=&arnumber=7036058}{Methodology for Standard Cell Compliance and Detailed Placement for Triple Patterning Lithography}'', 
        IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), vol.34, no.5, pp.726-739, 2015. 
}
%}}}
\end{description}


\textbf{Conference Papers}
\begin{description}[font=\normalfont]
%{{{
\item[{[C9]}]{
    Jiaojiao Ou, Bei Yu, Xiaoqing Xu, Joydeep Mitra, \textbf{Yibo Lin} and David Z. Pan, 
    ``DSAR: DSA aware Routing with Simultaneous DSA Guiding Pattern and Double Patterning Assignment'', 
    ACM International Symposium on Physical Design (ISPD), Portland, OR, Mar. 19–22, 2017
    (to appear)
}
\item[{[C8]}]{
    Yudong Tao, Changhao Yan, \textbf{Yibo Lin}, Shengguo Wang, David Z. Pan, and Xuan Zeng, 
    ``\href{http://dx.doi.org/10.1145/2966986.2966994}{A Novel Unified Dummy Fill Insertion Framework with SQP-Based Optimization Method}'', 
    IEEE/ACM International Conference on Computer-Aided Design (ICCAD), Austin, TX, Nov. 7-10, 2016
}
\item[{[C7]}]{
    \textbf{Yibo Lin}, Bei Yu, Xiaoqing Xu, Jhih-Rong Gao, Natarajan Viswanathan, Wen-Hao Liu, Zhuo Li, Charles J. Alpert and David Z. Pan, 
    ``\href{http://dx.doi.org/10.1145/2966986.2967055}{MrDP: Multiple-row Detailed Placement of Heterogeneous-sized Cells for Advanced Nodes}'', 
    IEEE/ACM International Conference on Computer-Aided Design (ICCAD), Austin, TX, Nov. 7-10, 2016
}
\item[{[C6]}]{
    \textbf{Yibo Lin}, Bei Yu, and David Z. Pan, 
   ``Detailed Placement In Advanced Technology Nodes: A Survey'', 
   IEEE International Conference on Solid -State and Integrated Circuit Technology (ICSICT), Hangzhou, China, Oct. 25-28, 2016
   (\textbf{Invited paper})
}
\item[{[C5]}]{
    \textbf{Yibo Lin}, Xiaoqing Xu, Bei Yu, Ross Baldick, and David Z. Pan, 
 ``\href{proceedings.spiedigitallibrary.org/proceeding.aspx?articleid=2505329}{Triple/Quadruple Patterning Layout Decomposition via Novel Linear Programming and Iterative Rounding}'', 
    SPIE Advanced Lithography Conference, San Jose, CA, Feb. 21-25, 2016
    (\textbf{Best Student Paper Award})
}
\item[{[C4]}]{
 \textbf{Yibo Lin}, Bei Yu, Yi Zou, Zhuo Li, Charles J. Alpert and David Z. Pan, 
 ``\href{http://ieeexplore.ieee.org/xpl/articleDetails.jsp?arnumber=7428009}{Stitch Aware Detailed Placement for Multiple E-Beam Lithography}'', 
    IEEE/ACM Asian and South Pacific Design Automation Conference (ASPDAC), Macau, Jan. 25-28, 2016.
}
\item[{[C3]}]{
 \textbf{Yibo Lin}, Bei Yu, Biying Xu and David Z. Pan, 
 ``\href{http://dl.acm.org/citation.cfm?id=2840875}{Triple Patterning Aware Detailed Placement Toward Zero Cross-Row Middle-of-Line Conflict}'', 
    IEEE/ACM International Conference on Computer-Aided Design (ICCAD), Austin, TX, Nov. 2-6, 2015.
}
\item[{[C2]}]{
 David Z. Pan, Lars Liebmann, Bei Yu, Xiaoqing Xu and \textbf{Yibo Lin}, 
 ``\href{http://dl.acm.org/citation.cfm?id=2744769.2747940}{Pushing Multiple Patterning in Sub-10nm: Are We Ready?}'', 
    ACM/IEEE Design Automation Conference (DAC), pp. 197:1-197:6, San Francisco, CA, June 7-11, 2015. 
    (\textbf{Invited Paper})
}
\item[{[C1]}]{
 \textbf{Yibo Lin}, Bei Yu and David Z. Pan, 
 ``\href{http://dl.acm.org/citation.cfm?id=2744769.2744850}{High Performance Dummy Fill Insertion with Coupling and Uniformity Constraints}'',
    ACM/IEEE Design Automation Conference (DAC), pp. 71:1-71:6, San Francisco, CA, June 7-11, 2015. 
}
%}}}
\end{description}


\end{rSection}

