\begin{rSection}{Invited Talks}

\textbf{Invited Talks at Conferences}
        
\begin{description}[font=\normalfont]
%{{{

\item[{[11]}]{
``Analyzing Timing in Shorter Time: A Journey through Heterogeneous Parallelism for Static Timing Analysis'', in IEEE International Conference on Solid-State and Integrated Circuit Technology (ICSICT), Zhuhai, China, Oct 22-25, 2024. 
}

\item[{[10]}]{
``Agile Analog IC Design: from Layout Automation to Circuit Synthesis'', in IEEE International Symposium on Radio-Frequency Integration Technology (RFIT), Chengdu, China, Aug 28-30, 2024. 
}

\item[{[9]}]{
``Workshop Talk: Empowering Physical Design of VLSI Circuits with Deep Learning: from Modeling to Optimization'', in International Symposium on Computer Architecture (ISCA), Buenos Aires, Argentina, Jun 29-Jul 3, 2024. 
}

\item[{[8]}]{
``Accelerating Routability and Timing Optimization with Open-Source AI4EDA Dataset CircuitNet and Heterogeneous Platforms'', in ACM/IEEE International Conference on Computer-Aided Design (ICCAD), San Francisco, Oct 29-Nov 2, 2023. 
}

\item[{[7]}]{
``Tutorial: Deep Learning Enabled Timing Optimization in Physical Design'', in ACM/IEEE Design Automation Conference (DAC), San Francisco, Jul 9-13, 2023. 
}

\item[{[6]}]{
``Timing Analysis and Optimization on Heterogeneous CPU-GPU Platforms'', in International Workshop on Logic \& Synthesis (IWLS), Virtual, Jul 18-21, 2022. 
}

\item[{[5]}]{
``DREAMPlace: Deep Learning Toolkit-Enabled GPU Acceleration for Modern VLSI Placement'', in ACM/IEEE Design Automation WebiNar (DAWN), Virtual, Apr 11-12, 2022. 
}

\item[{[4]}]{
``DREAMPlace 3.X: Exploring Advanced Constraints and Multi-GPU Acceleration'', in China Semiconductor Technology International Conference (CSTIC), Shanghai, China, Mar 14-15, 2021. 
}

\item[{[3]}]{
``Deep Learning for Mask Synthesis and Verification: A Survey'', in IEEE/ACM Asia and South Pacific Design Automation Conference (ASPDAC), Tokyo, Japan, Jan 18-21, 2021.
}

\item[{[2]}]{
``Tutorial: GPU Acceleration in VLSI Back-end Design: Overview and Case Studies'', in IEEE/ACM International Conference on Computer-Aided Design (ICCAD), Virtual, Nov 2-5, 2020. 
}

\item[{[1]}]{
``DREAMPlace 2.0: Open-Source GPU-Accelerated Global and Detailed Placement for Large-Scale VLSI Designs'', in China Semiconductor Technology International Conference (CSTIC), Shanghai, China, Jun 26, 2020. 
}

%}}}
\end{description}

\textbf{Invited Talks at Organizations}
        
\begin{description}[font=\normalfont]
%{{{

\item[{[13]}]{
``AI-Empowered Heterogeneous Computing for Physical Design Automation towards Timing Closure'', KAIST, Korea, Oct 21, 2024. 
}

\item[{[12]}]{
``AI-Empowered Heterogeneous Computing for Physical Design Automation towards Timing Closure'', Seoul National University, Korea, Sep 27, 2024. 
}

\item[{[11]}]{
``The Art of Formulation and Optimization in VLSI Placement for Diverse Design Scenarios'', Google DeepMind, Mountain View, California, Jul 29, 2024. 
}

\item[{[10]}]{
``AI-Empowered Heterogeneous Computing for Physical Design Automation'', Georgia Institute of Technology, Atlanta, Georgia, Jul 3, 2024. 
}

\item[{[9]}]{
``Deep Learning for Physical Design Automation of VLSI Circuits: Modeling, Optimization, and Datasets'', Synopsys, Armenia, Feb 5, 2024. 
}

\item[{[8]}]{
``Accelerating Timing Closure of IC Design with Heterogeneous Computing and Machine Intelligence'', University of Wisconsin, Madison, Nov 3, 2023. 
}

\item[{[7]}]{
``Accelerating Timing Closure of Integrated Circuits with Heterogeneous Computing and Machine Intelligence '', Arizona State University, Oct 27, 2023. 
}

\item[{[6]}]{
``Heterogenous Timing Analysis, Prediction, and Optimization of Integrated Circuits with Machine Intelligence '', National University of Singapore, Aug 29, 2023. 
}

\item[{[5]}]{
``Deep Learning for Backend Design Automation of VLSI Circuits: Modeling, Optimization, and Datasets'', Hong Kong University of Science and Technology, Apr 14, 2023. 
}

\item[{[4]}]{
``Deep Learning for Physical Design Automation of VLSI Circuits: Modeling, Optimization, and Datasets'', Chinese University of Hong Kong, Mar 23, 2023. 
}

\item[{[3]}]{
``Timing Analysis and Optimization on Heterogeneous CPU-GPU Platforms'', Synopsys, Armenia, Jan 30, 2023. 
}

\item[{[2]}]{
``Accelerating VLSI Physical Design with Parallel and Heterogeneous Computing'', Synopsys, Armenia, Jan 24, 2022. 
}

\item[{[1]}]{
``Machine Learning Based IC Backend Design and Acceleration'', Synopsys, Armenia, Apr 8, 2021. 
}

%}}}
\end{description}

\end{rSection}
