\documentclass[a4paper]{resume}  % Use the custom resume.cls style
\usepackage[UTF8]{ctex} % support Chinese characters
\setCJKmainfont[AutoFakeBold=true]{STFangsong}
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{enumitem}
\usepackage{url}
\usepackage{hyperref}
\usepackage{xcolor}
\hypersetup{
    colorlinks,
    linkcolor={red!50!black},
    citecolor={blue!50!black},
    urlcolor={blue!80!black}
}

\makeatletter

% Functional foreach construct 
% #1 - Function to call on each comma-separated item in #2
% #2 - Comma-separated list of items to pass as second parameter to function #1
\def\foreach#1#2{%
  \@foreach{#1}#2,\@end@token%
}

% Internal helper function - Eats one input
\def\@swallow#1{}

% Internal helper function - Checks the next character after #1 and 
% continues loop iteration if \@end@token is not found 
\def\@test@foreach#1{%
  \@ifnextchar\@end@token%
    {\@swallow}%
    {, \@foreach{#1}}%
}

% Internal helper function - Calls #1{#2} and recurses
% The magic of splitting the third parameter occurs in the pattern matching of the \def
\def\@foreach#1#2,#3\@end@token{%
  #1{#2}%
  \@test@foreach{#1}#3\@end@token%
}

\makeatother

\newcommand{\DefMacro}[2]{\expandafter\newcommand\csname rmk-#1\endcsname{#2}}
\newcommand{\UseMacro}[1]{\csname rmk-#1\endcsname}
\def\CiteMacro#1{[\foreach{\UseMacro}{#1}]}

\name{10 Selected Publications}
%
%\address{Assistant Professor \\ Department of Design Automation and Computing System}
%\address{School of Integrated Circuits, 5 Yiheyuan Road, Beijing, China, 100871 \\ Peking University}
%\address{yibolin@pku.edu.cn \\ www.yibolin.com}

\begin{document}

%\input{doc/repr_pubs}

Inverse chronological order. * denotes corresponding authors. 
Image quality may degrade due to compression of the PDF file for email.  

\begin{enumerate}
%{{{

\item{
        Yifan Chen, Zaiwen Wen, Yun Liang and \textbf{Yibo Lin}*, 
    ``\href{https://doi.org/10.1109/ICCAD57390.2023.10323700}{Stronger Mixed-Size Placement Backbone Considering Second-Order Information}'', 
    IEEE/ACM International Conference on Computer-Aided Design (ICCAD), San Francisco, CA, Oct 29-31, 2023.
}
\item{
        Haoyi Zhang, Xiaohan Gao, Haoyang Luo, Jiahao Song, Xiyuan Tang, Junhua Liu, \textbf{Yibo Lin}*, Runsheng Wang and Ru Huang, 
    ``\href{https://doi.org/10.23919/DATE56975.2023.10137296}{SAGERoute: Synergistic Analog Routing Considering Geometric and Electrical Constraints with Manual Design Compatibility}'', 
    IEEE/ACM Proceedings Design, Automation and Test in Europe (DATE), Antwerp, Belgium, Apr 17-19, 2023.
    (\textbf{Best Paper Award})
}
\item{
        Jing Mai, Jiarui Wang, Zhixiong Di and \textbf{Yibo Lin}*, 
    ``\href{https://doi.org/10.1109/TCAD.2023.3313101}{Multi-Electrostatic FPGA Placement Considering SLICEL-SLICEM Heterogeneity, Clock Feasibility, and Timing Optimization}'', 
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), Sep, 2023.
}
\item{
        Zizheng Guo, Tsung-Wei Huang and \textbf{Yibo Lin}*, 
    ``\href{https://doi.org/10.1109/TCAD.2023.3286261}{Accelerating Static Timing Analysis using CPU-GPU Heterogeneous Parallelism}'', 
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), Jun, 2023.
}
\item{
        Qipan Wang, Xiaohan Gao, \textbf{Yibo Lin}*, Runsheng Wang and Ru Huang, 
    ``\href{https://doi.org/10.1145/3508352.3549398}{DeePEB: A Neural Partial Differential Equation Solver for Post Exposure Baking Simulation in Lithography}'', 
    IEEE/ACM International Conference on Computer-Aided Design (ICCAD), San Diego, CA, Nov 01-03, 2022.
    (\textbf{Best Paper Nomination})
}
\item{
        Zizheng Guo and \textbf{Yibo Lin}*, 
    ``\href{https://doi.org/10.1145/3489517.3530486}{Differentiable-Timing-Driven Global Placement}'', 
    ACM/IEEE Design Automation Conference (DAC), San Francisco, CA, Jul 10-14, 2022.
}
\item{
        Siting Liu, Peiyu Liao, Zhitang Chen, Wenlong Lv, \textbf{Yibo Lin}* and Bei Yu*, 
    ``\href{https://doi.org/10.23919/DATE54114.2022.9774606}{FastGR: Global Routing on CPU-GPU with Heterogeneous Task Graph Scheduler}'', 
    IEEE/ACM Proceedings Design, Automation and Test in Europe (DATE), Antwerp, Belgium, Mar 14-23, 2022.
    (\textbf{Best Paper Award})
}
\item{
        Zizheng Guo, Jing Mai and \textbf{Yibo Lin}*, 
    ``\href{https://doi.org/10.1109/DAC18074.2021.9586149}{Ultrafast CPU/GPU Kernels for Density Accumulation in Placement}'', 
    ACM/IEEE Design Automation Conference (DAC), San Francisco, CA, Dec 05-09, 2021.
    
}
\item{
        Zizheng Guo, Tsung-Wei Huang and \textbf{Yibo Lin}*, 
    ``\href{https://doi.org/10.1109/DAC18074.2021.9586085}{A Provably Good and Practically Efficient Algorithm for Common Path Pessimism Removal in Large Designs}'', 
    ACM/IEEE Design Automation Conference (DAC), San Francisco, CA, Dec 05-09, 2021.
    
}
\item{
        \textbf{Yibo Lin}*, Zixuan Jiang, Jiaqi Gu, Wuxi Li, Shounak Dhar, Haoxing Ren, Brucek Khailany and David Z. Pan, 
    ``\href{https://doi.org/10.1109/TCAD.2020.3003843}{DREAMPlace: Deep Learning Toolkit-Enabled GPU Acceleration for Modern VLSI Placement}'', 
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), Apr, 2021.
    (\textbf{Best Paper Award})
}

%}}}
\end{enumerate}

\end{document}

