\begin{rSection}{发明专利列表}



\begin{description}[font=\normalfont, rightmargin=2em]
%{{{
    

\item[{[P18]}]{
        吴恒 ,  卢浩然 ,  江循 ,  孙嘉诚 ,  王润声 ,  \textbf{林亦波} ,  黄如, 
    ``半导体结构的制备方法、半导体结构、器件及设备'', 
    中国专利, CN2024101785421, Feb 09, 2024.
    (submitted)
}
            

\item[{[P17]}]{
        \textbf{林亦波} ,  郭资政 ,  张作栋 ,  江循 ,  王润声 ,  黄如, 
    ``电路门级逻辑仿真方法、装置、计算机设备和存储介质'', 
    中国专利, CN2023112735027, Jan 09, 2024.
    (submitted)
}
            

\item[{[P16]}]{
        余备 ,  廖培宇 ,  \textbf{林亦波}, 
    ``一种基于MoreauEnvelope近似线长模型的大规模解析布局方法'', 
    中国专利, CN2023111300780, Nov 28, 2023.
    (submitted)
}
            

\item[{[P15]}]{
        王润声 ,  张作栋 ,  \textbf{林亦波} ,  黄如, 
    ``一种基于解析模型的晶体管老化应力计算方法'', 
    中国专利, CN202310843291X, Oct 13, 2023.
    (submitted)
}
            

\item[{[P14]}]{
        \textbf{林亦波} ,  高笑涵 ,  张昊懿 ,  王润声 ,  黄如, 
    ``一种多驱动能力的集成电路标准单元版图迁移的方法'', 
    中国专利, CN2023101249631, Mar 28, 2023.
    
}
            

\item[{[P13]}]{
        \textbf{林亦波} ,  王启盼 ,  王润声 ,  黄如, 
    ``一种集成电路微带线传输线自动化分析设计方法'', 
    中国专利, CN2023100496576, Mar 17, 2023.
    
}
            

\item[{[P12]}]{
        \textbf{林亦波} ,  郭资政 ,  谷丰, 
    ``一种GPU加速构建最小直角斯坦纳树的芯片布线方法'', 
    中国专利, CN2022112858018, Jan 03, 2023.
    (submitted)
}
            

\item[{[P11]}]{
        \textbf{林亦波} ,  高笑涵 ,  张昊懿 ,  王润声 ,  黄如, 
    ``可处理电学和几何约束的模拟电路布线自动化方法及系统'', 
    中国专利, CN2022114229951, Dec 20, 2022.
    
}
            

\item[{[P10]}]{
        郭资政 ,  \textbf{林亦波} ,  黃琮蔚, 
    ``一种集成电路静态时序分析中的路径分析方法'', 
    中国专利, CN2021103772507, Oct 18, 2022.
    (submitted)
}
            

\item[{[P9]}]{
        \textbf{林亦波} ,  郭资政, 
    ``一种可微分时序驱动的芯片布局优化方法'', 
    中国专利, CN2022107930171, Aug 05, 2022.
    
}
            

\item[{[P8]}]{
        \textbf{林亦波} ,  张昊懿 ,  高笑涵 ,  王润声 ,  黄如, 
    ``一种用于模拟电路版图布线的交互式编辑方法及工具'', 
    中国专利, CN2022100363194, May 17, 2022.
    
}
            

\item[{[P7]}]{
        \textbf{林亦波} ,  麦景, 
    ``基于多电场模型的时钟驱动FPGA芯片全局布局方法'', 
    中国专利, CN2022102058942, Apr 12, 2022.
    
}
            

\item[{[P6]}]{
        \textbf{林亦波} ,  张作栋 ,  郭资政 ,  王润声 ,  黄如, 
    ``一种老化及涨落感知的动态时序分析方法'', 
    中国专利, CN2021115414669, Apr 5, 2022.
    (submitted)
}
            

\item[{[P5]}]{
        \textbf{林亦波} ,  张作栋 ,  郭资政 ,  王润声 ,  黄如, 
    ``一种基于事件传播的动态时序分析方法'', 
    中国专利, CN2021109930951, Dec 24, 2021.
    
}
            

\item[{[P4]}]{
        \textbf{林亦波} ,  郭资政 ,  黃琮蔚, 
    ``一种GPU加速计算的集成电路无悲观路径分析方法'', 
    中国专利, CN2021110703249, Dec 24, 2021.
    
}
            

\item[{[P3]}]{
        麦景 ,  郭资政 ,  \textbf{林亦波}, 
    ``一种集成电路设计中器件密度分布的计算方法'', 
    中国专利, CN2021105506486, Aug 27, 2021.
    
}
            

\item[{[P2]}]{
        高笑涵 ,  \textbf{林亦波} ,  刘鸣杰 ,  潘志刚, 
    ``一种交互式模拟电路版图编辑方法及系统'', 
    中国专利, CN2021101747163, Jun 18, 2021.
    
}
            

\item[{[P1]}]{
        郭资政 ,  黃琮蔚 ,  \textbf{林亦波}, 
    ``一种GPU加速计算的集成电路静态时序分析方法'', 
    中国专利, CN2020111436325, Jan 22, 2021.
    
}
            

%}}}
\end{description}
    

\end{rSection}


\begin{rSection}{著作及论文列表}



\textbf{书籍章节}
        

\begin{description}[font=\normalfont, rightmargin=2em]
%{{{
    

\item[{[B3]}]{
        \textbf{Yibo Lin}, Zizheng Guo and Jing Mai, 
    ``\href{https://doi.org/10.1007/978-3-031-13074-8}{Deep Learning Framework for Placement}'', 
    Machine Learning Applications in Electronic Design Automation, Springer, 2023, edited by Haoxing Ren and Jiang Hu.
    (\textbf{Invited Book Chapter})
}
            

\item[{[B2]}]{
        Haoyu Yang, \textbf{Yibo Lin} and Bei Yu, 
    ``\href{https://doi.org/10.1007/978-3-031-13074-8}{Machine Learning for Mask Synthesis and Verification}'', 
    Machine Learning Applications in Electronic Design Automation, Springer, 2023, edited by Haoxing Ren and Jiang Hu.
    (\textbf{Invited Book Chapter})
}
            

%}}}
\end{description}
    

\textbf{会议及期刊论文} (标*表示通讯作者)
        

            \underline{论文成果包括: DAC (23篇), ICCAD (16篇), IEEE TCAD (24篇), DATE (14篇), ...} 
    

\begin{description}[font=\normalfont, rightmargin=2em]
%{{{
    

\item[{[C172]}]{
        Tianxiang Zhu, Qipan Wang, \textbf{Yibo Lin}*, Runsheng Wang and Ru Huang, 
    ``MORE-Stress: Model Order Reduction based Efficient Numerical Algorithm for Thermal Stress Simulation of TSV Arrays in 2.5D/3D IC'', 
    IEEE/ACM Proceedings Design, Automation and Test in Europe (DATE), Lyon, France, Mar 31, 2025.
    
}
            

\item[{[C171]}]{
        Xizhe Shi, Zizheng Guo, \textbf{Yibo Lin}*, Runsheng Wang and Ru Huang, 
    ``Handling Latch Loops in Timing Analysis with Improved Complexity and Divergent Loop Detection'', 
    IEEE/ACM Proceedings Design, Automation and Test in Europe (DATE), Lyon, France, Mar 31, 2025.
    
}
            

\item[{[C170]}]{
        Haikang Diao, Haoyi Zhang, Jiahao Song, Haoyang Luo, \textbf{Yibo Lin}, Runsheng Wang, Yuan Wang and Xiyuan Tang*, 
    ``SEGA-DCIM: Design Space Exploration-Guided Automatic Digital CIM Compiler with Multiple Precision Support'', 
    IEEE/ACM Proceedings Design, Automation and Test in Europe (DATE), Lyon, France, Mar 31, 2025.
    
}
            

\item[{[C169]}]{
        Che Chang, Boyang Zhang, Cheng-Hsiang Chiu, Dian-Lun Lin, Yi-Hua Chung, Wan-Luan Lee, Zizheng Guo, \textbf{Yibo Lin} and Tsung-Wei Huang*, 
    ``PathGen: An Efficient Parallel Critical Path Generation Algorithm'', 
    IEEE/ACM Asia and South Pacific Design Automation Conference (ASPDAC), Tokyo, Japan, Jan, 2025.
    (accepted)
}
            

\item[{[C168]}]{
        Boyang Zhang, Che Chang, Cheng-Hsiang Chiu, Dian-Lun Lin, Yang Sui, Chih-Chun Chang, Yi-Hua Chung, Wan Luan Lee, Zizheng Guo, \textbf{Yibo Lin} and Tsung-Wei Huang*, 
    ``iTAP: An Incremental Task Graph Partitioner for Task-parallel Static Timing Analysis'', 
    IEEE/ACM Asia and South Pacific Design Automation Conference (ASPDAC), Tokyo, Japan, Jan, 2025.
    (accepted)
}
            

\item[{[J167]}]{
        Siting Liu, Ziyi Wang, Fangzhou Liu, \textbf{Yibo Lin}, Bei Yu* and Martin Wong, 
    ``\href{https://doi.org/10.1109/TCAD.2024.3506216}{Sign-off Timing Considerations via Concurrent Routing Topology Optimization}'', 
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), 2024.
    (accepted)
}
            

\item[{[C166]}]{
        Zizheng Guo, \textbf{Yibo Lin}*, Runsheng Wang and Ru Huang, 
    ``Analyzing Timing in Shorter Time: A Journey through Heterogeneous Parallelism for Static Timing Analysis'', 
    IEEE International Conference on Solid-State and Integrated Circuit Technology (ICSICT), Zhuhai, China, Oct 22-25, 2024.
    (\textbf{Invited paper})
}
            

\item[{[C165]}]{
        Qipan Wang, Xueqing Li, Tianyu Jia, \textbf{Yibo Lin}*, Runsheng Wang and Ru Huang, 
    ``ATPlace2.5D: Analytical Thermal-Aware Chiplet Placement Framework for Large-Scale 2.5D-IC'', 
    IEEE/ACM International Conference on Computer-Aided Design (ICCAD), New Jersey, Oct, 2024.
    
}
            

\item[{[C164]}]{
        Chunyuan Zhao, Zizheng Guo, Rui Wang, Zaiwen Wen, Yun Liang and \textbf{Yibo Lin}*, 
    ``HeLEM-GR: Heterogeneous Global Routing with Linearized Exponential Multiplier Method'', 
    IEEE/ACM International Conference on Computer-Aided Design (ICCAD), New Jersey, Oct, 2024.
    
}
            

\item[{[C163]}]{
        Zizheng Guo, Zuodong Zhang, Wuxi Li, Tsung-Wei Huang, Xizhe Shi, Yufan Du, \textbf{Yibo Lin}*, Runsheng Wang and Ru Huang, 
    ``HeteroExcept: A CPU-GPU Heterogeneous Algorithm to Accelerate Exception-aware Static Timing Analysis'', 
    IEEE/ACM International Conference on Computer-Aided Design (ICCAD), New Jersey, Oct, 2024.
    
}
            

\item[{[C162]}]{
        Xiaohan Gao, Haoyi Zhang, Bingyan Liu, \textbf{Yibo Lin}*, Runsheng Wang and Ru Huang, 
    ``Joint Placement Optimization for Hierarchical Analog/Mixed-Signal Circuits'', 
    IEEE/ACM International Conference on Computer-Aided Design (ICCAD), New Jersey, Oct, 2024.
    
}
            

\item[{[C161]}]{
        Yufan Du, Zizheng Guo, \textbf{Yibo Lin}*, Runsheng Wang and Ru Huang, 
    ``Fusion of Global Placement and Gate Sizing with Differentiable Optimization'', 
    IEEE/ACM International Conference on Computer-Aided Design (ICCAD), New Jersey, Oct, 2024.
    (\textbf{Best Paper Nomination})
}
            

\item[{[C160]}]{
        Tianxiang Zhu, Qipan Wang, \textbf{Yibo Lin}*, Runsheng Wang and Ru Huang, 
    ``FaStTherm: Fast and Stable Full-Chip Transient Thermal Predictor Considering Nonlinear Effects'', 
    IEEE/ACM International Conference on Computer-Aided Design (ICCAD), New Jersey, Oct, 2024.
    
}
            

\item[{[C159]}]{
        Jing Mai, Zuodong Zhang, \textbf{Yibo Lin}*, Runsheng Wang and Ru Huang, 
    ``MORPH: More Robust ASIC Placement for Hybrid Region Constraint Management'', 
    IEEE/ACM International Conference on Computer-Aided Design (ICCAD), New Jersey, Oct, 2024.
    
}
            

\item[{[J158]}]{
        Tsung-Yi Ho, Sadaf Khan, Jinwei Liu, Yi Liu, Zhengyuan Shi, Ziyi Wang, Qiang Xu*, Evangeline F.Y. Young, Bei Yu, Ziyang Zheng, Binwu Zhu, Keren Zhu, Yiqi Che, Yun Liang, \textbf{Yibo Lin}, Guojie Luo, Guangyu Sun, Runsheng Wang, Xinming Wei, Chenhao Xue, Haoyi Zhang, Zuodong Zhang, Yuxiang Zhao, Sunan Zou, Lei Chen, Yu Huang, Min Li, Dimitrios Tsaras, Mingxuan Yuan, Hui-Ling Zhen, Zhufei Chu, Wenji Fang, Xingquan Li and Zhiyao Xie, 
    ``\href{https://doi.org/10.1007/s11432-024-4155-7}{Large Circuit Models: Opportunities and Challenges}'', 
    Science China Information Sciences, Sep, 2024.
    
}
            

\item[{[J157]}]{
        Yuxuan Zhao, Peiyu Liao, Siting Liu, Jiaxi Jiang, \textbf{Yibo Lin} and Bei Yu*, 
    ``\href{https://doi.org/10.1109/TCAD.2024.3444716}{Analytical Heterogeneous Die-to-Die 3D Placement With Macros}'', 
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), Aug, 2024.
    (accepted)
}
            

\item[{[J156]}]{
        Xun Jiang, Jiarui Wang, Jing Mai, Zhixiong Di and \textbf{Yibo Lin}*, 
    ``\href{https://doi.org/10.1109/TCAD.2024.3447218}{A Robust FPGA Router With Optimization of High-Fanout Nets and Intra-CLB Connections}'', 
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), Aug, 2024.
    (accepted)
}
            

\item[{[C155]}]{
        Jiarui Wang, Xun Jiang and \textbf{Yibo Lin}*, 
    ``\href{https://doi.org/10.1145/3649329.3655900}{Top-Level Routing for Multiply-Instantiated Blocks with Topology Hashing}'', 
    ACM/IEEE Design Automation Conference (DAC), San Francisco, CA, Jun 23-27, 2024.
    
}
            

\item[{[C154]}]{
        Yufan Du, Zizheng Guo, Xun Jiang, Zhuomin Chai, Yuxiang Zhao, \textbf{Yibo Lin}*, Runsheng Wang and Ru Huang, 
    ``\href{https://doi.org/10.1145/3649329.3657349}{PowPrediCT: Cross-Stage Power Prediction with Circuit-Transformation-Aware Learning}'', 
    ACM/IEEE Design Automation Conference (DAC), San Francisco, CA, Jun 23-27, 2024.
    
}
            

\item[{[C153]}]{
        Haoyi Zhang, Jiahao Song, Xiaohan Gao, Xiyuan Tang, \textbf{Yibo Lin}*, Runsheng Wang and Ru Huang, 
    ``\href{https://doi.org/10.1145/3649329.3656229}{EasyACIM: An End-to-End Automated Analog CIM with Synthesizable Architecture and Agile Design Space Exploration}'', 
    ACM/IEEE Design Automation Conference (DAC), San Francisco, CA, Jun 23-27, 2024.
    
}
            

\item[{[C152]}]{
        Zichen Kong, Xiyuan Tang*, Wei Shi, Yiheng Du, \textbf{Yibo Lin} and Yuan Wang, 
    ``\href{https://doi.org/10.1145/3649329.3661850}{PVTSizing: A TuRBO-RL-Based Batch-Sampling Optimization Framework for PVT-Robust Analog Circuit Synthesis}'', 
    ACM/IEEE Design Automation Conference (DAC), San Francisco, CA, Jun 23-27, 2024.
    
}
            

\item[{[C151]}]{
        Yuan Pu, Fangzhou Liu, Yu Zhang, Zhuolun He, Kai-Yuan Chao, \textbf{Yibo Lin} and Bei Yu*, 
    ``\href{https://doi.org/10.1145/3649329.3656243}{Lesyn: Placement-aware Logic Resynthesis for Non-Integer Multiple-Cell-Height Designs}'', 
    ACM/IEEE Design Automation Conference (DAC), San Francisco, CA, Jun 23-27, 2024.
    
}
            

\item[{[C150]}]{
        Wan Luan Lee, Dian-Lun Lin, Tsung-Wei Huang*, Shui Jiang, Tsung-Yi Ho, \textbf{Yibo Lin} and Bei Yu, 
    ``\href{https://doi.org/10.1145/3649329.3656238}{G-kway: Multilevel GPU-Accelerated k-way Graph Partitioner}'', 
    ACM/IEEE Design Automation Conference (DAC), San Francisco, CA, Jun 23-27, 2024.
    
}
            

\item[{[C149]}]{
        Chenhao Xue, Chen Zhang, Xun Jiang,  Gao Zhutianya , \textbf{Yibo Lin} and Guangyu Sun*, 
    ``\href{https://doi.org/10.1145/3649329.3656221}{Oltron: Algorithm-Hardware Co-design for Outlier-Aware Quantization of LLMs with Inter-/Intra-Layer Adaptation}'', 
    ACM/IEEE Design Automation Conference (DAC), San Francisco, CA, Jun 23-27, 2024.
    
}
            

\item[{[C148]}]{
        Haoran Lu, Y Ge, ong , Xun Jiang, Jiacheng Sun, Wanyue Peng, Rui Guo, Ming Li, \textbf{Yibo Lin}, Runsheng Wang, Heng Wu* and Ru Huang, 
    ``\href{https://doi.org/10.1109/VLSITechnologyandCir46783.2024.10631460}{First Experimental Demonstration of Self-Aligned Flip FET (FFET): A Breakthrough Stacked Transistor Technology with 2.5T Design, Dual-Side Active and Interconnects}'', 
    IEEE Symposium on VLSI Technology and Circuits (VLSI), Honolulu, HI, Jun 16-20, 2024.
    
}
            

\item[{[J147]}]{
        Peiyu Liao, Yuxuan Zhao, Dawei Guo, \textbf{Yibo Lin} and Bei Yu*, 
    ``\href{https://doi.org/10.1109/TCAD.2023.3347293}{Analytical Die-to-Die 3D Placement With Bistratal Wirelength Model and GPU Acceleration}'', 
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), Jun, 2024.
    
}
            

\item[{[C146]}]{
        Xiaohan Gao, Haoyi Zhang, Zhu Pan, \textbf{Yibo Lin}*, Runsheng Wang and Ru Huang, 
    ``\href{https://doi.org/10.1109/ISEDA62518.2024.10617650}{Migrating Standard Cells for Multiple Drive Strengths by Routing Imitation}'', 
    IEEE/ACM International Symposium of EDA (ISEDA), Xi'an, China, May 10-13, 2024.
    
}
            

\item[{[C145]}]{
        Qipan Wang, Tianxiang Zhu, \textbf{Yibo Lin}*, Runsheng Wang and Ru Huang, 
    ``\href{https://doi.org/10.1109/ISEDA62518.2024.10617604}{ATSim3D: Towards Accurate Thermal Simulator for Heterogeneous 3D IC Systems Considering Nonlinear Leakage and Conductivity}'', 
    IEEE/ACM International Symposium of EDA (ISEDA), Xi'an, China, May 10-13, 2024.
    (\textbf{Honorable Mention Paper Award})
}
            

\item[{[C144]}]{
        Jing Mai, Jiarui Wang, Yifan Chen, Zizheng Guo, Xun Jiang, Yun Liang and \textbf{Yibo Lin}*, 
    ``\href{https://doi.org/10.1109/ISEDA62518.2024.10617535}{OpenPARF 3.0: Robust Multi-Electrostatics Based FPGA Macro Placement Considering Cascaded Macros Groups and Fence Regions}'', 
    IEEE/ACM International Symposium of EDA (ISEDA), Xi'an, China, May 10-13, 2024.
    (\textbf{Best Paper Award})
}
            

\item[{[C143]}]{
        Xun Jiang, Zhuomin Chai, Yuxiang Zhao, \textbf{Yibo Lin}*, Runsheng Wang and Ru Huang, 
    ``\href{https://openreview.net/pdf?id=nMFSUjxMIl}{CircuitNet 2.0: An Advanced Dataset for Promoting Machine Learning Innovations in Realistic Chip Design Environment}'', 
    International Conference on Learning Representations (ICLR), Vienna, Austria, May 7-11, 2024.
    
}
            

\item[{[J142]}]{
        Yufei Chen, Zizheng Guo, Runsheng Wang, Ru Huang, \textbf{Yibo Lin} and Cheng Zhuo, 
    ``\href{https://doi.org/10.1109/TCAD.2023.3342603}{Dynamic Supply Noise Aware Timing Analysis With JIT Machine Learning Integration}'', 
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), May, 2024.
    (accepted)
}
            

\item[{[C141]}]{
        Zizheng Guo, Tsung-Wei Huang, Zhou Jin, Cheng Zhuo, \textbf{Yibo Lin}*, Runsheng Wang and Ru Huang, 
    ``\href{https://ieeexplore.ieee.org/document/10546507}{Heterogeneous Static Timing Analysis with Advanced Delay Calculator}'', 
    IEEE/ACM Proceedings Design, Automation and Test in Europe (DATE), Valencia, Spain, Mar 24-28, 2024.
    
}
            

\item[{[C140]}]{
        Haoyi Zhang, Xiaohan Gao, Zilong Shen, Jiahao Song, Xiaoxu Cheng, Xiyuan Tang, \textbf{Yibo Lin}*, Runsheng Wang and Ru Huang, 
    ``\href{https://ieeexplore.ieee.org/document/10546542}{SAGERoute 2.0: Hierarchical Analog and Mixed Signal Routing Considering Versatile Routing Scenarios}'', 
    IEEE/ACM Proceedings Design, Automation and Test in Europe (DATE), Valencia, Spain, Mar 24-28, 2024.
    
}
            

\item[{[C139]}]{
        Yuan Pu, Tinghuan Chen, Zhuolun He, Chen Bai, Haisheng Zheng, \textbf{Yibo Lin} and Bei Yu*, 
    ``\href{https://doi.org/10.1145/3626184.3633321}{IncreMacro: Incremental Macro Placement Refinement}'', 
    ACM International Symposium on Physical Design (ISPD), Taipei, Mar 12-15, 2024.
    (\textbf{Best Paper Nomination})
}
            

\item[{[C138]}]{
        Yu Zhang, Yuan Pu, Fangzhou Liu, Peiyu Liao, Kaiyuan Chao, Keren Zhu, \textbf{Yibo Lin} and Bei Yu*, 
    ``\href{https://doi.org/10.1145/3626184.3633320}{Multi-Electrostatics Based Placement for Non-Integer Multiple-Height Cells}'', 
    ACM International Symposium on Physical Design (ISPD), Taipei, Mar 12-15, 2024.
    
}
            

\item[{[C137]}]{
        Siting Liu, Jiaxi Jiang, Zhuolun He, Ziyi Wang, \textbf{Yibo Lin} and Bei Yu*, 
    ``\href{https://doi.org/10.1145/3626184.3633322}{Routing-aware Legal Hybrid Bonding Terminal Assignment for 3D Face-to-Face Stacked ICs}'', 
    ACM International Symposium on Physical Design (ISPD), Taipei, Mar 12-15, 2024.
    
}
            

\item[{[J136]}]{
        Zhixiong Di*, Runzhe Tao, Jing Mai, Lin Chen and \textbf{Yibo Lin}, 
    ``\href{https://doi.org/10.1109/TCSI.2023.3340554}{LEAPS: Topological-Layout-Adaptable Multi-Die FPGA Placement for Super Long Line Minimization}'', 
    IEEE Transactions on Circuits and Systems I, Mar, 2024.
    
}
            

\item[{[J135]}]{
        Jing Mai, Jiarui Wang, Zhixiong Di and \textbf{Yibo Lin}*, 
    ``\href{https://doi.org/10.1109/TCAD.2023.3313101}{Multielectrostatic FPGA Placement Considering SLICEL-SLICEM Heterogeneity, Clock Feasibility, and Timing Optimization}'', 
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), Feb, 2024.
    
}
            

\item[{[C134]}]{
        Cheng-Hsiang Chiu, Zhicheng Xiong, Zizheng Guo, Tsung-Wei Huang* and \textbf{Yibo Lin}, 
    ``\href{https://doi.org/10.1145/3635035.3635037}{An Efficient Task-parallel Pipeline Programming Framework}'', 
    International Conference on High-Performance Computing in Asia-Pacific Region (HPC Asia), Nagoya, Japan, Jan, 2024.
    
}
            

\item[{[J133]}]{
        Zizheng Guo, Tsung-Wei Huang and \textbf{Yibo Lin}*, 
    ``\href{https://doi.org/10.1109/TCAD.2023.3286261}{Accelerating Static Timing Analysis using CPU-GPU Heterogeneous Parallelism}'', 
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), Dec, 2023.
    
}
            

\item[{[J132]}]{
        Zhuomin Chai, Yuxiang Zhao, Wei Liu, \textbf{Yibo Lin}*, Runsheng Wang and Ru Huang, 
    ``\href{https://doi.org/10.1109/TCAD.2023.3287970}{CircuitNet: An Open-Source Dataset for Machine Learning in VLSI CAD Applications with Improved Domain-Specific Evaluation Metric and Learning Strategies}'', 
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), Dec, 2023.
    
}
            

\item[{[J131]}]{
        Zuodong Zhang, Zizheng Guo, \textbf{Yibo Lin}*, Runsheng Wang and Ru Huang, 
    ``\href{https://doi.org/10.1109/TCAD.2023.3255167}{AVATAR: An Aging- and Variation-Aware Dynamic Timing Analyzer for Error-Efficient Computing}'', 
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), Nov, 2023.
    
}
            

\item[{[J130]}]{
        Guannan Guo, Tsung-Wei Huang*, \textbf{Yibo Lin}, Zizheng Guo, Sushma Yellapragada and Martin Wong, 
    ``\href{https://doi.org/10.1109/TCAD.2023.3272274}{A GPU-accelerated Framework for Path-based Timing Analysis}'', 
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), Nov, 2023.
    
}
            

\item[{[C129]}]{
        Yifan Chen, Zaiwen Wen, Yun Liang and \textbf{Yibo Lin}*, 
    ``\href{https://doi.org/10.1109/ICCAD57390.2023.10323700}{Stronger Mixed-Size Placement Backbone Considering Second-Order Information}'', 
    IEEE/ACM International Conference on Computer-Aided Design (ICCAD), San Francisco, CA, Oct 29-31, 2023.
    
}
            

\item[{[J128]}]{
        Peiyu Liao, Dawei Guo, Zizheng Guo, Siting Liu, Zhitang Chen, Wenlong Lv, \textbf{Yibo Lin}* and Bei Yu*, 
    ``\href{https://doi.org/10.1109/TCAD.2023.3240132}{DREAMPlace 4.0: Timing-driven Placement with Momentum-based Net Weighting and Lagrangian-based Refinement}'', 
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), Oct, 2023.
    
}
            

\item[{[J127]}]{
        Xiaohan Gao, Haoyi Zhang, Siyuan Ye, Mingjie Liu, David Z. Pan, Linxiao Shen, Runsheng Wang, \textbf{Yibo Lin}* and Ru Huang, 
    ``\href{https://doi.org/10.1007/s11432-022-3878-5}{Post-Layout Simulation Driven Analog Circuit Sizing}'', 
    SCIENCE CHINA Information Sciences, Oct, 2023.
    
}
            

\item[{[C126]}]{
        Jing Mai, Jiaru Wang, Zhixiong Di, Guojie Luo, Yun Liang and \textbf{Yibo Lin}*, 
    ``\href{https://doi.org/10.1109/ASICON58565.2023.10396248}{OpenPARF: An Open-Source Placement and Routing Framework for Large-Scale Heterogeneous FPGAs with Deep Learning Toolkit}'', 
    International Conference on ASIC (ASICON), Nanjing, China, Oct, 2023.
    (\textbf{Invited paper})
}
            

\item[{[C125]}]{
        Xun Jiang, Zizheng Guo, Zhuomin Chai, Yuxiang Zhao, \textbf{Yibo Lin}*, Runsheng Wang and Ru Huang, 
    ``\href{https://doi.org/10.1109/ICCAD57390.2023.10323938}{Accelerating Routability and Timing Optimization with Open-Source AI4EDA Dataset CircuitNet and Heterogeneous Platforms}'', 
    IEEE/ACM International Conference on Computer-Aided Design (ICCAD), San Francisco, CA, Oct, 2023.
    (\textbf{Invited paper})
}
            

\item[{[C124]}]{
        Kexing Zhou, Yun Liang*, \textbf{Yibo Lin}, Runsheng Wang and Ru Huang, 
    ``\href{https://doi.org/10.1145/3613424.3614301}{Khronos: Fusing Memory Access for Improved Hardware RTL Simulation}'', 
    IEEE/ACM International Symposium on Microarchitecture (MICRO), Toronto, Canada, Oct, 2023.
    
}
            

\item[{[J123]}]{
        Binwu Zhu, Xinyun Zhang, \textbf{Yibo Lin}, Bei Yu and Martin Wong, 
    ``\href{https://doi.org/10.1145/3594666}{DRC-SG 2.0: Efficient Design Rule Checking Script Generation via Key Information Extraction}'', 
    ACM Transactions on Design Automation of Electronic Systems (TODAES), Sep, 2023.
    
}
            

\item[{[C122]}]{
        Zizheng Guo, Zuodong Zhang, Xun Jiang, Wuxi Li, \textbf{Yibo Lin}*, Runsheng Wang and Ru Huang, 
    ``\href{https://doi.org/10.1109/DAC56929.2023.10247907}{General-Purpose Gate-Level Simulation with Partition-Agnostic Parallelism}'', 
    ACM/IEEE Design Automation Conference (DAC), San Francisco, CA, Jul 9-13, 2023.
    
}
            

\item[{[C121]}]{
        Qipan Wang, Ping Liu, Ligguo Jiang, Mingjie Liu, \textbf{Yibo Lin}*, Runsheng Wang and Ru Huang, 
    ``\href{https://doi.org/10.1109/DAC56929.2023.10247759}{MTL-Designer: An Integrated Flow for Analysis and Synthesis of Microstrip Transmission Line}'', 
    ACM/IEEE Design Automation Conference (DAC), San Francisco, CA, Jul 9-13, 2023.
    
}
            

\item[{[C120]}]{
        Peiyu Liao, Hongduo Liu, \textbf{Yibo Lin}*, Bei Yu* and Martin Wong, 
    ``\href{https://doi.org/10.1109/DAC56929.2023.10247712}{On a Moreau Envelope Wirelength Model for Analytical Global Placement}'', 
    ACM/IEEE Design Automation Conference (DAC), San Francisco, CA, Jul 9-13, 2023.
    
}
            

\item[{[C119]}]{
        Siting Liu, Ziyi Wang, Fangzhou Liu, \textbf{Yibo Lin}, Bei Yu and Martin Wong*, 
    ``\href{https://doi.org/10.1109/DAC56929.2023.10247794}{Concurrent Sign-off Timing Optimization via Deep Steiner Points Refinement}'', 
    ACM/IEEE Design Automation Conference (DAC), San Francisco, CA, Jul 9-13, 2023.
    
}
            

\item[{[C118]}]{
        Su Zheng, Lancheng Zou, Siting Liu, \textbf{Yibo Lin}, Bei Yu and Martin Wong*, 
    ``\href{https://doi.org/10.1109/DAC56929.2023.10247660}{Mitigating Distribution Shift for Congestion Optimization in Global Placement}'', 
    ACM/IEEE Design Automation Conference (DAC), San Francisco, CA, Jul 9-13, 2023.
    
}
            

\item[{[C117]}]{
        Yu Zhang, Yifan Chen, Zhonglin Xie, Hong Xu, Zaiwen Wen, \textbf{Yibo Lin}* and Bei Yu*, 
    ``\href{https://doi.org/10.1109/DAC56929.2023.10247846}{LRSDP: Low-Rank SDP for Triple Patterning Lithography Layout Decomposition}'', 
    ACM/IEEE Design Automation Conference (DAC), San Francisco, CA, Jul 9-13, 2023.
    
}
            

\item[{[J116]}]{
        Siting Liu, Yuan Pu, Peiyu Liao, Hongzhong Wu, Rui Zhang, Zhitang Chen, Wenlong Lv, \textbf{Yibo Lin}* and Bei Yu*, 
    ``\href{https://doi.org/10.1109/TCAD.2022.3217668}{FastGR: Global Routing on CPU-GPU with Heterogeneous Task Graph Scheduler}'', 
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), Jul, 2023.
    
}
            

\item[{[C115]}]{
        Yuxiang Zhao, Zhuomin Chai, \textbf{Yibo Lin}*, Runsheng Wang and Ru Huang, 
    ``\href{https://doi.org/10.1109/ISEDA59274.2023.10218656}{HybridNet: Dual-Branch Fusion of Geometrical and Topological Views for VLSI Congestion Prediction}'', 
    IEEE/ACM International Symposium of EDA (ISEDA), Nanjing, China, May 8-11, 2023.
    
}
            

\item[{[C114]}]{
        Haoyi Zhang, Xiaohan Gao, \textbf{Yibo Lin}*, Runsheng Wang and Ru Huang, 
    ``\href{https://doi.org/10.1109/ISEDA59274.2023.10218434}{Multi-Scenario Analog and Mixed-Signal Circuit Routing with Agile Human Interaction}'', 
    IEEE/ACM International Symposium of EDA (ISEDA), Nanjing, China, May 8-11, 2023.
    
}
            

\item[{[C113]}]{
        Haoyi Zhang, Xiaohan Gao, Haoyang Luo, Jiahao Song, Xiyuan Tang, Junhua Liu, \textbf{Yibo Lin}*, Runsheng Wang and Ru Huang, 
    ``\href{https://doi.org/10.23919/DATE56975.2023.10137296}{SAGERoute: Synergistic Analog Routing Considering Geometric and Electrical Constraints with Manual Design Compatibility}'', 
    IEEE/ACM Proceedings Design, Automation and Test in Europe (DATE), Antwerp, Belgium, Apr 17-19, 2023.
    (\textbf{Best Paper Award})
}
            

\item[{[C112]}]{
        Zuodong Zhang, Meng Li*, \textbf{Yibo Lin}, Runsheng Wang and Ru Huang, 
    ``\href{https://doi.org/10.23919/DATE56975.2023.10137254}{READ: Reliability-Enhanced Accelerator Dataflow Optimization using Critical Input Pattern Reduction}'', 
    IEEE/ACM Proceedings Design, Automation and Test in Europe (DATE), Antwerp, Belgium, Apr 17-19, 2023.
    
}
            

\item[{[J111]}]{
        Xiaohan Gao, Haoyi Zhang, Mingjie Liu, Linxiao Shen, David Z. Pan, \textbf{Yibo Lin}*, Runsheng Wang and Ru Huang, 
    ``\href{https://doi.org/10.1109/TCAD.2022.3190234}{Interactive Analog Layout Editing with Instant Placement and Routing Legalization}'', 
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), Mar, 2023.
    
}
            

\item[{[J110]}]{
        \textbf{Yibo Lin}, Avi Ziv and Haoxing Ren, 
    ``\href{https://doi.org/10.1145/3586208}{Introduction to the Special Issue on Machine Learning for CAD/EDA}'', 
    ACM Transactions on Design Automation of Electronic Systems (TODAES), Mar, 2023.
    
}
            

\item[{[J109]}]{
        Xinfa Zhang, Zuodong Zhang, \textbf{Yibo Lin}*, Zhigang Ji*, Runsheng Wang and Ru Huang, 
    ``\href{https://doi.org/10.1109/TCSII.2022.3212123}{Efficient Aging-Aware Standard Cell Library Characterization Based on Sensitivity Analysis}'', 
    IEEE Transactions on Circuits and Systems II: Express Briefs, Feb, 2023.
    
}
            

\item[{[C108]}]{
        Yifan Chen, Jing Mai, Xiaohan Gao, Muhan Zhang and \textbf{Yibo Lin}*, 
    ``\href{https://doi.org/10.1145/3566097.3567899}{MacroRank: Ranking Macro Placement Solutions Leveraging Translation Equivariancy}'', 
    IEEE/ACM Asia and South Pacific Design Automation Conference (ASPDAC), Tokyo, Japan, Jan 16-19, 2023.
    
}
            

\item[{[C107]}]{
        Jiarui Wang, Jing Mai, Zhixiong Di and \textbf{Yibo Lin}*, 
    ``\href{https://doi.org/10.1145/3566097.3567898}{A Robust FPGA Router with Concurrent Intra-CLB Rerouting}'', 
    IEEE/ACM Asia and South Pacific Design Automation Conference (ASPDAC), Tokyo, Japan, Jan 16-19, 2023.
    
}
            

\item[{[J106]}]{
        Junchi Yan*, Xianglong Lyu, Ruoyu Cheng and \textbf{Yibo Lin}, 
    ``Towards Machine Learning for Placement and Routing in Chip Design: a Methodological Overview'', 
    arXiv preprint, 2022.
    
}
            

\item[{[J105]}]{
        Wei Li, Jialu Xia, Yuzhe Ma, Jialu Li, \textbf{Yibo Lin} and Bei Yu*, 
    ``\href{https://doi.org/10.1109/TCAD.2022.3140729}{Adaptive Layout Decomposition with Graph Embedding Neural Networks}'', 
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), Nov, 2022.
    
}
            

\item[{[C104]}]{
        Zizheng Guo, Feng Gu and \textbf{Yibo Lin}*, 
    ``\href{https://doi.org/10.1145/3508352.3549434}{GPU-Accelerated Rectilinear Steiner Tree Generation}'', 
    IEEE/ACM International Conference on Computer-Aided Design (ICCAD), San Diego, CA, Nov 01-03, 2022.
    
}
            

\item[{[C103]}]{
        Qipan Wang, Xiaohan Gao, \textbf{Yibo Lin}*, Runsheng Wang and Ru Huang, 
    ``\href{https://doi.org/10.1145/3508352.3549398}{DeePEB: A Neural Partial Differential Equation Solver for Post Exposure Baking Simulation in Lithography}'', 
    IEEE/ACM International Conference on Computer-Aided Design (ICCAD), San Diego, CA, Nov 01-03, 2022.
    (\textbf{Best Paper Nomination})
}
            

\item[{[C102]}]{
        \textbf{Yibo Lin}*, Xiaohan Gao, Haoyi Zhang, Runsheng Wang and Ru Huang, 
    ``\href{https://doi.org/10.1109/ICSICT55466.2022.9963217}{Intelligent and Interactive Analog Layout Design Automation}'', 
    IEEE International Conference on Solid-State and Integrated Circuit Technology (ICSICT), Nanjing, China, Oct 25-28, 2022.
    (\textbf{Invited paper})
}
            

\item[{[J101]}]{
        Zizheng Guo, Mingwei Yang, Tsung-Wei Huang and \textbf{Yibo Lin}*, 
    ``\href{https://doi.org/10.1109/TCAD.2021.3124758}{A Provably Good and Practically Efficient Algorithm for Common Path Pessimism Removal in Large Designs}'', 
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), Oct, 2022.
    
}
            

\item[{[J100]}]{
        Martin Rapp, Hussam Amrouch, \textbf{Yibo Lin}, Bei Yu, David Z. Pan, Marilyn Wolf and Jörg Henkel*, 
    ``\href{https://doi.org/10.1109/TCAD.2021.3124762}{MLCAD: A Survey of Research in Machine Learning for CAD}'', 
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), Oct, 2022.
    (\textbf{Invited Keynote paper})
}
            

\item[{[C99]}]{
        Binwu Zhu, Xinyun Zhang, \textbf{Yibo Lin}, Bei Yu* and Martin Wong, 
    ``\href{https://doi.org/10.1145/3551901.3556494}{Efficient Design Rule Checking Script Generation via Key Information Extraction}'', 
    ACM/IEEE Workshop on Machine Learning for CAD (MLCAD), Snowbird, Utah, Sep 12-13, 2022.
    
}
            

\item[{[J98]}]{
        \textbf{Yibo Lin}, Tong Qu, Zongqing Lu, Yajuan Su* and Yayi Wei*, 
    ``\href{https://doi.org/10.1109/TCAD.2021.3117505}{Asynchronous Reinforcement Learning Framework and Knowledge Transfer for Net Order Exploration in Detailed Routing}'', 
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), Sep, 2022.
    
}
            

\item[{[J97]}]{
        Zhuomin Chai, Yuxiang Zhao, \textbf{Yibo Lin}*, Wei Liu, Runsheng Wang and Ru Huang, 
    ``\href{https://doi.org/10.1007/s11432-022-3571-8}{CircuitNet: An Open-Source Dataset for Machine Learning Applications in Electronic Design Automation (EDA)}'', 
    SCIENCE CHINA Information Sciences, Sep, 2022.
    
}
            

\item[{[C96]}]{
        Jing Mai, Yibai Meng, Zhixiong Di and \textbf{Yibo Lin}*, 
    ``\href{https://doi.org/10.1145/3489517.3530568}{Multi-Electrostatic FPGA Placement Considering SLICEL-SLICEM Heterogeneity and Clock Feasibility}'', 
    ACM/IEEE Design Automation Conference (DAC), San Francisco, CA, Jul 10-14, 2022.
    
}
            

\item[{[C95]}]{
        Zizheng Guo and \textbf{Yibo Lin}*, 
    ``\href{https://doi.org/10.1145/3489517.3530486}{Differentiable-Timing-Driven Global Placement}'', 
    ACM/IEEE Design Automation Conference (DAC), San Francisco, CA, Jul 10-14, 2022.
    
}
            

\item[{[C94]}]{
        Zizheng Guo, Mingjie Liu, Jiaqi Gu, Shuhan Zhang, David Z. Pan and \textbf{Yibo Lin}*, 
    ``\href{https://doi.org/10.1145/3489517.3530597}{A Timing Engine Inspired Graph Neural Network Model for Pre-Routing Slack Prediction}'', 
    ACM/IEEE Design Automation Conference (DAC), San Francisco, CA, Jul 10-14, 2022.
    
}
            

\item[{[C93]}]{
        Zuodong Zhang, Zizheng Guo, \textbf{Yibo Lin}*, Runsheng Wang and Ru Huang, 
    ``\href{https://doi.org/10.1145/3489517.3530530}{AVATAR: An Aging- and Variation-Aware Dynamic Timing Analyzer for Application-based DVAFS}'', 
    ACM/IEEE Design Automation Conference (DAC), San Francisco, CA, Jul 10-14, 2022.
    
}
            

\item[{[C92]}]{
        Bowen Wang, Guibao Shen, Dong Li, Jianye Hao, Wulong Liu, Yu Huang, Hongzhong Wu, \textbf{Yibo Lin}, Guangyong Chen and Pheng Ann Heng, 
    ``LHNN: Lattice Hypergraph Neural Network for VLSI Congestion Prediction'', 
    ACM/IEEE Design Automation Conference (DAC), San Francisco, CA, Jul 10-14, 2022.
    
}
            

\item[{[J91]}]{
        Tsung-Wei Huang*, Dian-Lun Lin, Chun-Xun Lin and \textbf{Yibo Lin}, 
    ``\href{https://doi.org/10.1109/TPDS.2021.3104255}{Taskflow: A Lightweight Parallel and Heterogeneous Task Graph Computing System}'', 
    IEEE Transactions on Parallel and Distributed Systems (TPDS), Jun, 2022.
    
}
            

\item[{[C90]}]{
        Zuodong Zhang, Zizheng Guo, \textbf{Yibo Lin}*, Runsheng Wang and Ru Huang, 
    ``\href{https://doi.org/10.23919/DATE54114.2022.9774642}{EventTimer: Fast and Accurate Event-Based Dynamic Timing Analysis}'', 
    IEEE/ACM Proceedings Design, Automation and Test in Europe (DATE), Antwerp, Belgium, Mar 14-23, 2022.
    
}
            

\item[{[C89]}]{
        Siting Liu, Peiyu Liao, Zhitang Chen, Wenlong Lv, \textbf{Yibo Lin}* and Bei Yu*, 
    ``\href{https://doi.org/10.23919/DATE54114.2022.9774606}{FastGR: Global Routing on CPU-GPU with Heterogeneous Task Graph Scheduler}'', 
    IEEE/ACM Proceedings Design, Automation and Test in Europe (DATE), Antwerp, Belgium, Mar 14-23, 2022.
    (\textbf{Best Paper Award})
}
            

\item[{[C88]}]{
        Peiyu Liao, Siting Liu, Zhitang Chen, Wenlong Lv, \textbf{Yibo Lin}* and Bei Yu*, 
    ``\href{https://doi.org/10.23919/DATE54114.2022.9774725}{DREAMPlace 4.0: Timing-driven Global Placement with Momentum-based Net Weighting}'', 
    IEEE/ACM Proceedings Design, Automation and Test in Europe (DATE), Antwerp, Belgium, Mar 14-23, 2022.
    
}
            

\item[{[C87]}]{
        Haoyu Yang, Kit Fung, Yuxuan Zhao, \textbf{Yibo Lin} and Bei Yu*, 
    ``\href{https://doi.org/10.23919/DATE54114.2022.9774671}{Mixed-Cell-Height Legalization on CPU-GPU Heterogeneous Systems}'', 
    IEEE/ACM Proceedings Design, Automation and Test in Europe (DATE), Antwerp, Belgium, Mar 14-23, 2022.
    
}
            

\item[{[C86]}]{
        Xun Jiang, \textbf{Yibo Lin} and Zhongfeng Wang*, 
    ``\href{https://doi.org/10.1109/ASP-DAC52403.2022.9712533}{FPGA-Accelerated Maze Routing Kernel for VLSI Designs}'', 
    IEEE/ACM Asia and South Pacific Design Automation Conference (ASPDAC), Virtual Conference, Jan 17-20, 2022.
    
}
            

\item[{[C85]}]{
        Kexing Zhou, Zizheng Guo, Tsung-Wei Huang and \textbf{Yibo Lin}*, 
    ``\href{https://doi.org/10.1109/ASP-DAC52403.2022.9712566}{Efficient Critical Paths Search Algorithm using Mergeable Heap}'', 
    IEEE/ACM Asia and South Pacific Design Automation Conference (ASPDAC), Virtual Conference, Jan 17-20, 2022.
    
}
            

\item[{[J84]}]{
        Yibai Meng, Wuxi Li, \textbf{Yibo Lin}* and David Z. Pan, 
    ``\href{https://doi.org/10.1109/TCAD.2021.3053191}{elfPlace: Electrostatics-based Placement for Large-Scale Heterogeneous FPGAs}'', 
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), Jan, 2022.
    
}
            

\item[{[C83]}]{
        Zizheng Guo, Tsung-Wei Huang and \textbf{Yibo Lin}*, 
    ``\href{https://doi.org/10.1109/DAC18074.2021.9586085}{A Provably Good and Practically Efficient Algorithm for Common Path Pessimism Removal in Large Designs}'', 
    ACM/IEEE Design Automation Conference (DAC), San Francisco, CA, Dec 05-09, 2021.
    
}
            

\item[{[C82]}]{
        Guannan Guo, Tsung-Wei Huang*, \textbf{Yibo Lin} and Martin Wong, 
    ``\href{https://doi.org/10.1109/DAC18074.2021.9586316}{GPU-accelerated Path-based Timing Analysis}'', 
    ACM/IEEE Design Automation Conference (DAC), San Francisco, CA, Dec 05-09, 2021.
    
}
            

\item[{[C81]}]{
        Zizheng Guo, Jing Mai and \textbf{Yibo Lin}*, 
    ``\href{https://doi.org/10.1109/DAC18074.2021.9586149}{Ultrafast CPU/GPU Kernels for Density Accumulation in Placement}'', 
    ACM/IEEE Design Automation Conference (DAC), San Francisco, CA, Dec 05-09, 2021.
    
}
            

\item[{[C80]}]{
        Xiaohan Gao, Mingjie Liu, David Z. Pan and \textbf{Yibo Lin}*, 
    ``\href{https://doi.org/10.1109/DAC18074.2021.9586234}{Interactive Analog Layout Editing with Instant Placement Legalization}'', 
    ACM/IEEE Design Automation Conference (DAC), San Francisco, CA, Dec 05-09, 2021.
    
}
            

\item[{[J79]}]{
        \textbf{Yibo Lin}*, 
    ``\href{https://dl.ccf.org.cn/article/articleDetail.html?type=xhtx_thesis&_ack=1&id=5743150191429632}{模拟电路版图自动化与智能设计}'', 
    中国计算机学会通讯, Dec, 2021.
    
}
            

\item[{[J78]}]{
        Wei Li, Yuzhe Ma, Qi Sun,  Zhang Lu , \textbf{Yibo Lin}, Iris Hui-Ru Jiang, Bei Yu* and David Z. Pan, 
    ``\href{https://doi.org/10.1109/TCAD.2020.3042175}{OpenMPL: An Open Source Layout Decomposer}'', 
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), Nov, 2021.
    
}
            

\item[{[C77]}]{
        Zizheng Guo, Tsung-Wei Huang and \textbf{Yibo Lin}*, 
    ``\href{https://doi.org/10.1109/ICCAD51958.2021.9643457}{HeteroCPPR: Accelerating Common Path Pessimism Removal with Heterogeneous CPU-GPU Parallelism}'', 
    IEEE/ACM International Conference on Computer-Aided Design (ICCAD), Virtual Conference, Nov 01-04, 2021.
    
}
            

\item[{[C76]}]{
        Guannan Guo, Tsung-Wei Huang*, \textbf{Yibo Lin} and Martin Wong, 
    ``\href{https://doi.org/10.1109/ICCAD51958.2021.9643504}{GPU-accelerated Critical Path Generation with Path Constraints}'', 
    IEEE/ACM International Conference on Computer-Aided Design (ICCAD), Virtual Conference, Nov 01-04, 2021.
    
}
            

\item[{[C75]}]{
        Tong Qu, \textbf{Yibo Lin}, Tianyang Gai, Xiaojing Su, Shuhan Wang, Bojie Ma, Yajuan Su* and Yayi Wei*, 
    ``\href{https://doi.org/10.1117/12.2601685}{Litho-Aware Redundant Local-Loop Insertion Framework With Convolutional Neural Network}'', 
    Proceedings of SPIE, San Jose, CA, Sep 27, 2021.
    
}
            

\item[{[J74]}]{
        Tsung-Wei Huang*, \textbf{Yibo Lin}, Chun-Xun Lin, Guannan Guo and Martin Wong, 
    ``\href{https://doi.org/10.1109/TCAD.2020.3025075}{Cpp-Taskflow: A General-purpose Parallel Task Programming System at Scale}'', 
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), Aug, 2021.
    
}
            

\item[{[J73]}]{
        \textbf{Yibo Lin}*, Zixuan Jiang, Jiaqi Gu, Wuxi Li, Shounak Dhar, Haoxing Ren, Brucek Khailany and David Z. Pan, 
    ``\href{https://doi.org/10.1109/TCAD.2020.3003843}{DREAMPlace: Deep Learning Toolkit-Enabled GPU Acceleration for Modern VLSI Placement}'', 
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), Apr, 2021.
    (\textbf{Best Paper Award})
}
            

\item[{[J72]}]{
        Junzhe Cai, Changhao Yan*, Yudong Tao, \textbf{Yibo Lin}, Sheng-Guo Wang, David Z. Pan and Xuan Zeng, 
    ``\href{https://doi.org/10.1109/TCAD.2020.3001380}{A Novel and Unified Full-chip CMP Model Aware Dummy Fill Insertion Framework with SQP-Based Optimization Method}'', 
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), Mar, 2021.
    
}
            

\item[{[J71]}]{
        Mohamed Baker Alawieh, \textbf{Yibo Lin}, Zaiwei Zhang, Meng Li, Qixing Huang and David Z. Pan*, 
    ``\href{https://doi.org/10.1109/TCAD.2020.2995338}{GAN-SRAF: Sub-Resolution Assist Feature Generation using Generative Adversarial Networks}'', 
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), Feb, 2021.
    
}
            

\item[{[J70]}]{
        \textbf{Yibo Lin}*, Xiaohan Gao, Tinghuan Chen and Bei Yu*, 
    ``\href{https://doi.org/10.19816/j.cnki.10-1594/tn.2021.02.011}{机器学习辅助数字集成电路后端设计方法}'', 
    微纳电子与智能制造, Feb, 2021.
    
}
            

\item[{[J69]}]{
        Cheng Zhuo*, Zizheng Guo, Xiao Dong, Qing He and \textbf{Yibo Lin}, 
    ``\href{https://doi.org/ 10.19816/j.cnki.10-1594/tn.2021.02.001}{先进工艺下的数字签核}'', 
    微纳电子与智能制造, Feb, 2021.
    
}
            

\item[{[C68]}]{
        Tong Qu, \textbf{Yibo Lin}, Zongqing Lu, Yajuan Su* and Yayi Wei*, 
    ``\href{https://doi.org/10.23919/DATE51398.2021.9474007}{Asynchronous Reinforcement Learning Framework for Net Order Exploration in Detailed Routing}'', 
    IEEE/ACM Proceedings Design, Automation and Test in Europe (DATE), Virtual Conference, Feb 01-05, 2021.
    
}
            

\item[{[C67]}]{
        Siting Liu, Qi Sun, Peiyu Liao, \textbf{Yibo Lin} and Bei Yu*, 
    ``\href{https://doi.org/10.23919/DATE51398.2021.9473959}{Global Placement with Deep Learning-Enabled Explicit Routability Optimization}'', 
    IEEE/ACM Proceedings Design, Automation and Test in Europe (DATE), Virtual Conference, Feb 01-05, 2021.
    
}
            

\item[{[C66]}]{
        Hongjia Li, Mengshu Sun, Tianyun Zhang, Olivia Chen, Nobuyuki Yoshikawa, Bei Yu, Yanzhi Wang* and \textbf{Yibo Lin}, 
    ``\href{https://doi.org/10.23919/DATE51398.2021.9474259}{Towards AQFP-Capable Physical Design Automation}'', 
    IEEE/ACM Proceedings Design, Automation and Test in Europe (DATE), Virtual Conference, Feb 01-05, 2021.
    
}
            

\item[{[C65]}]{
        Xiaohan Gao, Chenhui Deng, Mingjie Liu, Zhiru Zhang, David Z. Pan and \textbf{Yibo Lin}*, 
    ``\href{https://doi.org/10.1145/3394885.3431545}{Layout Symmetry Annotation for Analog Circuits with Graph Neural Networks}'', 
    IEEE/ACM Asia and South Pacific Design Automation Conference (ASPDAC), Tokyo, Japan, Jan 18-21, 2021.
    
}
            

\item[{[C64]}]{
        \textbf{Yibo Lin}*, 
    ``\href{https://doi.org/10.1145/3394885.3431624}{Deep Learning for Mask Synthesis and Verification: A Survey}'', 
    IEEE/ACM Asia and South Pacific Design Automation Conference (ASPDAC), Tokyo, Japan, Jan 18-21, 2021.
    (\textbf{Invited paper})
}
            

\item[{[J63]}]{
        \textbf{Yibo Lin}*, Wuxi Li, Jiaqi Gu, Haoxing Ren, Brucek Khailany and David Z. Pan, 
    ``\href{https://doi.org/10.1109/TCAD.2020.2971531}{ABCDPlace: Accelerated Batch-based Concurrent Detailed Placement on Multi-threaded CPUs and GPUs}'', 
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), Dec, 2020.
    
}
            

\item[{[C62]}]{
        Jiaqi Gu, Zixuan Jiang, \textbf{Yibo Lin} and David Z. Pan*, 
    ``\href{https://doi.org/10.1145/3400302.3415691}{DREAMPlace 3.0: Multi-Electrostatics Based Robust VLSI Placement with Region Constraints}'', 
    IEEE/ACM International Conference on Computer-Aided Design (ICCAD), Nov 2-5, 2020.
    
}
            

\item[{[C61]}]{
        Zizheng Guo, Tsung-Wei Huang and \textbf{Yibo Lin}*, 
    ``\href{https://doi.org/10.1145/3400302.3415631}{GPU-Accelerated Static Timing Analysis}'', 
    IEEE/ACM International Conference on Computer-Aided Design (ICCAD), Nov 2-5, 2020.
    
}
            

\item[{[C60]}]{
        \textbf{Yibo Lin}*, 
    ``\href{https://doi.org/10.1145/3400302.3415765}{GPU Acceleration in VLSI Back-end Design: Overview and Case Studies}'', 
    IEEE/ACM International Conference on Computer-Aided Design (ICCAD), Nov 2-5, 2020.
    (\textbf{Invited tutorial})
}
            

\item[{[C59]}]{
        Wei Ye, Mohamed Baker Alawieh, Yuki Watanabe, Shigeki Nojima, \textbf{Yibo Lin} and David Z. Pan*, 
    ``\href{https://doi.org/10.1145/3372780.3375565}{TEMPO: Fast Mask Topography Effect Modeling with Deep Learning}'', 
    ACM International Symposium on Physical Design (ISPD), Taipei, Taiwan, Sep 20-23, 2020.
    (\textbf{Best Paper Award})
}
            

\item[{[J58]}]{
        Jing Chen, Mohamed Baker Alawieh, \textbf{Yibo Lin}, Maolin Zhang, Jun Zhang, Yufeng Guo* and David Z. Pan, 
    ``\href{https://doi.org/10.1109/LED.2020.3013571}{Automatic Selection of Structure Parameters of Silicon on Insulator Lateral Power Device Using Bayesian Optimization}'', 
    IEEE Electron Device Letters (EDL), Sep, 2020.
    
}
            

\item[{[C57]}]{
        Wei Li, Jialu Xia, Yuzhe Ma, Jialu Li, \textbf{Yibo Lin} and Bei Yu*, 
    ``\href{https://doi.org/10.1109/DAC18072.2020.9218706}{Adaptive Layout Decomposition with Graph Embedding Neural Networks}'', 
    ACM/IEEE Design Automation Conference (DAC), San Francisco, Jul 19-23, 2020.
    
}
            

\item[{[J56]}]{
        Ying Chen, \textbf{Yibo Lin}, Rui Chen, Lisong Dong, Ruixuan Wu, Tianyang Gai, Le Ma, Yajuan Su* and Yayi Wei*, 
    ``\href{https://doi.org/10.1364/OE.394590}{EUV Multilayer Defect Characterization via Cycle-Consistent Learning}'', 
    Optics Express, Jun, 2020.
    
}
            

\item[{[C55]}]{
        \textbf{Yibo Lin}*, David Z. Pan, Haoxing Ren and Brucek Khailany, 
    ``DREAMPlace 2.0: Open-Source GPU-Accelerated Global and Detailed Placement for Large-Scale VLSI Designs'', 
    China Semiconductor Technology International Conference (CSTIC), Shanghai, China, Jun, 2020.
    (\textbf{Invited paper})
}
            

\item[{[J54]}]{
        Jing Chen, Mohamed Baker Alawieh, \textbf{Yibo Lin}, Maolin Zhang, Jun Zhang, Yufeng Guo* and David Z. Pan, 
    ``\href{https://doi.org/10.1109/ACCESS.2020.2970966}{Powernet: SOI Lateral Power Device Breakdown Prediction With Deep Neural Networks}'', 
    IEEE Access, Feb, 2020.
    
}
            

\item[{[J53]}]{
        Ying Chen, \textbf{Yibo Lin}, Lisong Dong, Tianyang Gai, Rui Chen, Yajuan Su*, Yayi Wei* and David Z. Pan, 
    ``\href{https://dx.doi.org/10.1117/1.JMM.18.4.043506}{SoulNet: Ultrafast Optical Source Optimization Utilizing Generative Neural Networks for Advanced Lithography}'', 
    Journal of Micro/Nanolithography, MEMS, and MOEMS (JM3), Nov, 2019.
    
}
            

%}}}
\end{description}
    

\begin{description}[font=\normalfont, rightmargin=2em]
%{{{
    \item \textbf{================ 以下为博士及博士后期间发表内容 ================}
%}}}
\end{description}
        

\textbf{书籍章节}
        

\begin{description}[font=\normalfont, rightmargin=2em]
%{{{
    

\item[{[B1]}]{
        \textbf{Yibo Lin} and David Z. Pan, 
    ``\href{http://dx.doi.org/10.1007/978-3-030-04666-8_4}{Machine Learning in Physical Verification, Mask Synthesis, and Physical Design}'', 
    Machine Learning in VLSI Computer-Aided Design, Springer, 2018, edited by Abe Elfedel, Duane Boning and Xin Li.
    (\textbf{Invited Book Chapter})
}
            

%}}}
\end{description}
    

\textbf{会议及期刊论文} (标*表示通讯作者)
        

            \underline{论文成果包括: DAC (7篇), ICCAD (7篇), IEEE TCAD (10篇), DATE (1篇), ...} 
    

\begin{description}[font=\normalfont, rightmargin=2em]
%{{{
    

\item[{[J52]}]{
        Hao Chen, Mingjie Liu, Biying Xu, Keren Zhu, Xiyuan Tang, Shaolan Li, \textbf{Yibo Lin}, Nan Sun and David Z. Pan*, 
    ``\href{https://doi.org/10.1109/MDAT.2020.3024153}{MAGICAL: An Open-Source Fully Automated Analog IC Layout System from Netlist to GDSII}'', 
    IEEE Design \& Test, Apr, 2021.
    
}
            

\item[{[C51]}]{
        Rachel Selina Rajarathnam, \textbf{Yibo Lin}, Yier Jin and David Z. Pan*, 
    ``\href{https://doi.org/10.1109/HOST45689.2020.9300272}{ReGDS: A Reverse Engineering Framework from GDSII to Gate-level Netlist}'', 
    IEEE International Workshop on Hardware-Oriented Security and Trust (HOST), San Jose, CA, May 4, 2020.
    
}
            

\item[{[C50]}]{
        Mingjie Liu, Wuxi Li, Keren Zhu, Biying Xu, \textbf{Yibo Lin}, Linxiao Shen, Xiyuan Tang, Nan Sun and David Z. Pan*, 
    ``S3DET: Detecting System Symmetry Constraints for Analog Circuits with Graph Similarity'', 
    IEEE/ACM Asia and South Pacific Design Automation Conference (ASPDAC), Jan 13-16, 2020.
    (\textbf{Best Paper Nomination})
}
            

\item[{[C49]}]{
        Mohamed Baker Alawieh, Wuxi Li, \textbf{Yibo Lin}, Love Singhal, Mahesh Iyer and David Z. Pan*, 
    ``High-Definition Routing Congestion Prediction for Large-Scale FPGAs'', 
    IEEE/ACM Asia and South Pacific Design Automation Conference (ASPDAC), Jan 13-16, 2020.
    
}
            

\item[{[C48]}]{
        Wuxi Li, \textbf{Yibo Lin} and David Z. Pan*, 
    ``\href{https://doi.org/10.1109/ICCAD45719.2019.8942075}{elfPlace: Electrostatics-based Placement for Large-Scale Heterogeneous FPGAs}'', 
    IEEE/ACM International Conference on Computer-Aided Design (ICCAD), Westminster, CO, Nov 4-7, 2019.
    
}
            

\item[{[C47]}]{
        Keren Zhu, Mingjie Liu, \textbf{Yibo Lin}, Biying Xu, Shaolan Li, Xiyuan Tang, Nan Sun and David Z. Pan*, 
    ``\href{https://doi.org/10.1109/ICCAD45719.2019.8942164}{GeniusRoute: A New Analog Routing Paradigm Using Generative Neural Network Guidance}'', 
    IEEE/ACM International Conference on Computer-Aided Design (ICCAD), Westminster, CO, Nov 4-7, 2019.
    
}
            

\item[{[C46]}]{
        Chengyue Gong, Zixuan Jiang, Dilin Wang, \textbf{Yibo Lin}, Qiang Liu and David Z. Pan*, 
    ``\href{https://doi.org/10.1109/ICCAD45719.2019.8942147}{Mixed Precision Neural Architecture Search for Energy Efficient Deep Learning}'', 
    IEEE/ACM International Conference on Computer-Aided Design (ICCAD), Westminster, CO, Nov 4-7, 2019.
    
}
            

\item[{[C45]}]{
        Biying Xu, Keren Zhu, Mingjie Liu, \textbf{Yibo Lin}, Shaolan Li, Xiyuan Tang, Nan Sun and David Z. Pan*, 
    ``\href{https://doi.org/10.1109/ICCAD45719.2019.8942060}{MAGICAL: Toward Fully Automated Analog IC Layout Leveraging Human and Machine Intelligence}'', 
    IEEE/ACM International Conference on Computer-Aided Design (ICCAD), Westminster, CO, Nov 4-7, 2019.
    (\textbf{Invited paper})
}
            

\item[{[J44]}]{
        \textbf{Yibo Lin}, Meng Li, Yuki Watanabe, Taiki Kimura, Tetsuaki Matsunawa, Shigeki Nojima and David Z. Pan*, 
    ``\href{https://doi.org/10.1109/TCAD.2018.2864251}{Data Efficient Lithography Modeling with Transfer Learning and Active Data Selection}'', 
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), Oct, 2019.
    
}
            

\item[{[C43]}]{
        Wei Li, Yuzhe Ma, Qi Sun, \textbf{Yibo Lin}, Iris Hui-Ru Jiang, Bei Yu and David Z Pan, 
    ``\href{https://arxiv.org/abs/1809.07554}{OpenMPL: An Open Source Layout Decomposer}'', 
    International Conference on ASIC (ASICON), Chongqing, China, Oct, 2019.
    (\textbf{Invited paper})
}
            

\item[{[C42]}]{
        \textbf{Yibo Lin}, Shounak Dhar, Wuxi Li, Haoxing Ren, Brucek Khailany and David Z. Pan*, 
    ``\href{https://doi.org/10.1145/3316781.3317803}{DREAMPlace: Deep Learning Toolkit-Enabled GPU Acceleration for Modern VLSI Placement}'', 
    ACM/IEEE Design Automation Conference (DAC), Las Vegas, NV, Jun 2-6, 2019.
    (\textbf{Best Paper Award})
}
            

\item[{[C41]}]{
        Wei Ye, Mohamed Baker Alawieh, \textbf{Yibo Lin} and David Z. Pan*, 
    ``\href{https://doi.org/10.1145/3316781.3317852}{LithoGAN: End-to-End Lithography Modeling with Generative Adversarial Networks}'', 
    ACM/IEEE Design Automation Conference (DAC), Las Vegas, NV, Jun 2-6, 2019.
    (\textbf{Best Paper Nomination})
}
            

\item[{[C40]}]{
        Biying Xu, \textbf{Yibo Lin}, Xiyuan Tang, Shaolan Li, Linxiao Shen, Nan Sun and David Z. Pan*, 
    ``\href{https://doi.org/10.1145/3316781.3317930}{WellGAN: Generative-Adversarial-Network-Guided Well Generation for Analog/Mixed-Signal Circuit Layout}'', 
    ACM/IEEE Design Automation Conference (DAC), Las Vegas, NV, Jun 2-6, 2019.
    
}
            

\item[{[C39]}]{
        Mohamed Baker Alawieh, \textbf{Yibo Lin}, Zaiwei Zhang, Meng Li, Qixing Huang and David Z. Pan*, 
    ``\href{https://doi.org/10.1145/3316781.3317832}{GAN-SRAF: Sub-Resolution Assist Feature Generation Using Conditional Generative Adversarial Networks}'', 
    ACM/IEEE Design Automation Conference (DAC), Las Vegas, NV, Jun 2-6, 2019.
    
}
            

\item[{[C38]}]{
        \textbf{Yibo Lin}, Zhao Song and Lin F. Yang*, 
    ``\href{https://arxiv.org/abs/1812.10244}{Towards a Theoretical Understanding of Hashing-Based Neural Nets}'', 
    International Conference on Artificial Intelligence and Statistics (AISTATS), Okinawa, Japan, Apr 16-18, 2019.
    
}
            

\item[{[C37]}]{
        Biying Xu, Shaolan Li, Chak-Wa Pui, Derong Liu, Linxiao Shen, \textbf{Yibo Lin}, Nan Sun and David Z. Pan*, 
    ``\href{https://doi.org/10.1145/3299902.3309751}{Device Layer-Aware Analytical Placement for Analog Circuits}'', 
    ACM International Symposium on Physical Design (ISPD), San Francisco, CA, Apr 14-17, 2019.
    (\textbf{Best Paper Nomination})
}
            

\item[{[J36]}]{
        Ying Chen, \textbf{Yibo Lin}, Tianyang Gai, Yajuan Su*, Yayi Wei* and David Z. Pan, 
    ``\href{https://doi.org/10.1109/TCAD.2019.2912948}{Semi-Supervised Hotspot Detection with Self-Paced Multi-Task Learning}'', 
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), Apr, 2019.
    
}
            

\item[{[C35]}]{
        Wei Ye, Mohamed Baker Alawieh, Meng Li, \textbf{Yibo Lin} and David Z. Pan*, 
    ``\href{https://doi.org/10.23919/DATE.2019.8714960}{Litho-GPA: Gaussian Process Assurance for Lithography Hotspot Detection}'', 
    IEEE/ACM Proceedings Design, Automation and Test in Europe (DATE), Florence, Italy, Mar 25-29, 2019.
    
}
            

\item[{[J34]}]{
        Jing Chen, \textbf{Yibo Lin}, Yufeng Guo, Maolin Zhang, Mohamed Baker Alawieh and David Z. Pan*, 
    ``\href{https://doi.org/10.1117/1.JMM.18.1.013507}{Lithography Hotspot Detection Using a Double Inception Module Architecture}'', 
    Journal of Micro/Nanolithography, MEMS, and MOEMS (JM3), Mar, 2019.
    
}
            

\item[{[C33]}]{
        Ying Chen, \textbf{Yibo Lin}, Tianyang Gai, Yajuan Su*, Yayi Wei* and David Z. Pan, 
    ``\href{https://doi.org/10.1145/3287624.3287685}{Semi-Supervised Hotspot Detection with Self-Paced Multi-Task Learning}'', 
    IEEE/ACM Asia and South Pacific Design Automation Conference (ASPDAC), Tokyo, Japan, Jan 21-24, 2019.
    
}
            

\item[{[C32]}]{
        Wei Ye, Mohamed Baker Alawieh, \textbf{Yibo Lin} and David Z. Pan*, 
    ``\href{https://doi.org/10.1145/3287624.3287688}{Tackling Signal Electromigration with Learning-Based Detection and Multistage Mitigation}'', 
    IEEE/ACM Asia and South Pacific Design Automation Conference (ASPDAC), Tokyo, Japan, Jan 21-24, 2019.
    
}
            

\item[{[C31]}]{
        Wei Ye, \textbf{Yibo Lin}, Meng Li, Qiang Liu and David Z. Pan*, 
    ``\href{https://doi.org/10.1145/3287624.3288746}{LithoROC: Lithography Hotspot Detection with Explicit ROC Optimization}'', 
    IEEE/ACM Asia and South Pacific Design Automation Conference (ASPDAC), Tokyo, Japan, Jan 21-24, 2019.
    (\textbf{Invited paper})
}
            

\item[{[C30]}]{
        \textbf{Yibo Lin}, Mohamed Baker Alawieh, Wei Ye and David Z. Pan*, 
    ``\href{https://doi.org/10.1109/TEST.2018.8624733}{Machine Learning for Yield Learning and Optimization}'', 
    IEEE International Test Conference (ITC), Phoenix, Arizona, Oct, 2018.
    (\textbf{Invited paper})
}
            

\item[{[J29]}]{
        \textbf{Yibo Lin}, Bei Yu, Meng Li and David Z. Pan*, 
    ``\href{https://doi.org/10.1109/TCAD.2017.2760511}{Layout Synthesis for Topological Quantum Circuits with 1D and 2D Architectures}'', 
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), Aug, 2018.
    
}
            

\item[{[J28]}]{
        Meng Li, Bei Yu, \textbf{Yibo Lin}, Xiaoqing Xu, Wuxi Li and David Z Pan, 
    ``\href{https://doi.org/10.1109/TCAD.2018.2859402}{A practical split manufacturing framework for trojan prevention via simultaneous wire lifting and cell insertion}'', 
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), Jul, 2018.
    
}
            

\item[{[C27]}]{
        Jiong Zhang, \textbf{Yibo Lin}, Zhao Song and Inderjit S Dhillon*, 
    ``\href{https://arxiv.org/pdf/1803.06585.pdf}{Learning Long Term Dependencies via Fourier Recurrent Units}'', 
    International Conference on Machine Learning (ICML), Stockholm, Sweden, Jun 10-15, 2018.
    
}
            

\item[{[J26]}]{
        Xiaoqing Xu, \textbf{Yibo Lin}, Meng Li, Tetsuaki Matsunawa, Shigeki Nojima, Chikaaki Kodama, Toshiya Kotani and David Z. Pan*, 
    ``\href{https://doi.org/10.1109/TCAD.2017.2748029}{Subresolution Assist Feature Generation With Supervised Data Learning}'', 
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), Jun, 2018.
    
}
            

\item[{[J25]}]{
        \textbf{Yibo Lin}, Bei Yu, Xiaoqing Xu, Jhih-Rong Gao, Natarajan Viswanathan, Wen-Hao Liu, Zhuo Li, Charles J Alpert and David Z. Pan*, 
    ``\href{https://doi.org/10.1109/TCAD.2017.2748025}{MrDP: Multiple-row detailed placement of heterogeneous-sized cells for advanced nodes}'', 
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), Jun, 2018.
    
}
            

\item[{[J24]}]{
        Wuxi Li, \textbf{Yibo Lin}, Meng Li, Shounak Dhar and David Z. Pan*, 
    ``\href{https://doi.org/10.1145/3174849}{UTPlaceF 2.0: A High-Performance Clock-Aware FPGA Placement Engine}'', 
    ACM Transactions on Design Automation of Electronic Systems (TODAES), Jun, 2018.
    
}
            

\item[{[C23]}]{
        \textbf{Yibo Lin}, Yuki Watanabe, Taiki Kimura, Tetsuaki Matsunawa, Shigeki Nojima, Meng Li and David Z. Pan*, 
    ``\href{https://doi.org/10.1145/3177540.3178242}{Data Efficient Lithography Modeling with Residual Neural Networks and Transfer Learning}'', 
    ACM International Symposium on Physical Design (ISPD), Monterey, CA, Mar 25-28, 2018.
    
}
            

\item[{[C22]}]{
        Meng Li, Bei Yu, \textbf{Yibo Lin}, Xiaoqing Xu, Wuxi Li and David Z. Pan*, 
    ``\href{https://doi.org/10.1109/ASPDAC.2018.8297316}{A Practical Split Manufacturing Framework for Trojan Prevention via Simultaneous Wire Lifting and Cell Insertion}'', 
    IEEE/ACM Asia and South Pacific Design Automation Conference (ASPDAC), Jeju, Korea, Jan 22-25, 2018.
    
}
            

\item[{[C21]}]{
        Che-Lun Hsu, Shaofeng Guo, \textbf{Yibo Lin}, Xiaoqing Xu, Meng Li, Runsheng Wang, Ru Huang and David Z Pan, 
    ``\href{https://doi.org/10.1109/ASPDAC.2018.8297298}{Layout-dependent aging mitigation for critical path timing}'', 
    IEEE/ACM Asia and South Pacific Design Automation Conference (ASPDAC), Jeju, Korea, Jan 22-25, 2018.
    
}
            

\item[{[C20]}]{
        \textbf{Yibo Lin}, Peter Debacker, Darko Trivkovic, Ryoung-han Kim, Praveen Raghavan and David Z. Pan*, 
    ``\href{https://doi.org/10.1109/ICCD.2017.72}{Patterning Aware Design Optimization of Selective Etching in N5 and Beyond}'', 
    IEEE International Conference on Computer Design (ICCD), Boston, MA, Nov 5-8, 2017.
    
}
            

\item[{[C19]}]{
        \textbf{Yibo Lin}, Xiaoqing Xu, Jiaojiao Ou and David Z Pan, 
    ``\href{http://dx.doi.org/10.1117/12.2282943}{Machine learning for mask/wafer hotspot detection and mask synthesis}'', 
    Photomask Technology, Oct 16, 2017.
    (\textbf{Invited paper})
}
            

\item[{[J18]}]{
        \textbf{Yibo Lin}, Bei Yu and David Z. Pan*, 
    ``\href{http://dx.doi.org/10.1109/TCAD.2016.2638452}{High performance dummy fill insertion with coupling and uniformity constraints}'', 
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), Sep, 2017.
    
}
            

\item[{[C17]}]{
        Wei Ye, \textbf{Yibo Lin}, Xiaoqing Xu, Wuxi Li, Yiwei Fu, Yongsheng Sun, Canhui Zhan and David Z. Pan*, 
    ``\href{https://doi.org/10.1109/ISLPED.2017.8009178}{Placement Mitigation Techniques for Power Grid Electromigration}'', 
    IEEE International Symposium on Low Power Electronics and Design (ISLPED), Taipei, Jul 24-26, 2017.
    
}
            

\item[{[J16]}]{
        \textbf{Yibo Lin}, Bei Yu, Biying Xu and David Z. Pan*, 
    ``\href{http://dx.doi.org/10.1109/TCAD.2017.2648843}{Triple patterning aware detailed placement toward zero cross-row middle-of-line conflict}'', 
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), Jul, 2017.
    
}
            

\item[{[J15]}]{
        Xiaoqing Xu, \textbf{Yibo Lin}, Meng Li, Jiaojiao Ou, Brian Cline and David Z. Pan*, 
    ``\href{http://dx.doi.org/10.1109/TCAD.2017.2651811}{Redundant local-Loop insertion for unidirectional routing}'', 
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), Jul, 2017.
    
}
            

\item[{[C14]}]{
        Xiaoqing Xu, \textbf{Yibo Lin}, Vinicius Livramento and David Z. Pan*, 
    ``\href{https://doi.org/10.1145/3061639.3062214}{Concurrent Pin Access Optimization for Unidirectional Routing}'', 
    ACM/IEEE Design Automation Conference (DAC), Austin, TX, Jun 18-22, 2017.
    
}
            

\item[{[J13]}]{
        \textbf{Yibo Lin}, Bei Yu, Yi Zou, Zhuo Li, Charles J Alpert and David Z. Pan*, 
    ``\href{http://dx.doi.org/10.1016/j.vlsi.2017.02.004}{Stitch aware detailed placement for multiple e-beam lithography}'', 
    Integration, the VLSI Journal, Jun, 2017.
    (\textbf{Best Paper Award})
}
            

\item[{[J12]}]{
        \textbf{Yibo Lin}, Xiaoqing Xu, Bei Yu, Ross Baldick and David Z. Pan*, 
    ``\href{http://dx.doi.org/10.1117/1.JMM.16.2.023507}{Triple/quadruple patterning layout decomposition via linear programming and iterative rounding}'', 
    Journal of Micro/Nanolithography, MEMS, and MOEMS (JM3), Jun, 2017.
    
}
            

\item[{[C11]}]{
        Jiaojiao Ou, Bei Yu, Xiaoqing Xu, Joydeep Mitra, \textbf{Yibo Lin} and David Z. Pan*, 
    ``\href{https://doi.org/10.1145/3036669.3036677}{DSAR: DSA aware routing with simultaneous DSA guiding pattern and double patterning assignment}'', 
    ACM International Symposium on Physical Design (ISPD), Portland, OR, Mar 19-22, 2017.
    
}
            

\item[{[C10]}]{
        \textbf{Yibo Lin}, Bei Yu, Xiaoqing Xu, Jhih-Rong Gao, Natarajan Viswanathan, Wen-Hao Liu, Zhuo Li, Charles J Alpert and David Z. Pan*, 
    ``\href{http://dx.doi.org/10.1145/2966986.2967055}{MrDP: Multiple-row detailed placement of heterogeneous-sized cells for advanced nodes}'', 
    IEEE/ACM International Conference on Computer-Aided Design (ICCAD), Austin, TX, Nov 7-10, 2016.
    
}
            

\item[{[C9]}]{
        Yudong Tao, Changhao Yan*, \textbf{Yibo Lin}, Sheng-Guo Wang, David Z. Pan and Xuan Zeng, 
    ``\href{http://dx.doi.org/10.1145/2966986.2966994}{A novel unified dummy fill insertion framework with SQP-based optimization method}'', 
    IEEE/ACM International Conference on Computer-Aided Design (ICCAD), Austin, TX, Nov 7-10, 2016.
    
}
            

\item[{[C8]}]{
        \textbf{Yibo Lin}, Bei Yu and David Z. Pan*, 
    ``\href{https://doi.org/10.1109/ICSICT.2016.7999056}{Detailed placement in advanced technology nodes: a survey}'', 
    IEEE International Conference on Solid-State and Integrated Circuit Technology (ICSICT), Hangzhou, China, Oct 25-28, 2016.
    (\textbf{Invited paper})
}
            

\item[{[J7]}]{
        Bei Yu, Xiaoqing Xu, Subhendu Roy, \textbf{Yibo Lin}, Jiaojiao Ou and David Z. Pan*, 
    ``\href{http://link.springer.com/article/10.1007%2Fs11432-016-5560-6}{Design for manufacturability and reliability in extreme-scaling {VLSI}}'', 
    Science China Information Sciences, May, 2016.
    (\textbf{Invited paper})
}
            

\item[{[C6]}]{
        \textbf{Yibo Lin}, Xiaoqing Xu, Bei Yu, Ross Baldick and David Z. Pan*, 
    ``\href{http://dx.doi.org/10.1117/12.2218628}{Triple/quadruple patterning layout decomposition via novel linear programming and iterative rounding}'', 
    Proceedings of SPIE, San Jose, CA, Feb 21-25, 2016.
    (\textbf{Best Student Paper Award})
}
            

\item[{[C5]}]{
        \textbf{Yibo Lin}, Bei Yu, Yi Zou, Zhuo Li, Charles J Alpert and David Z. Pan*, 
    ``\href{http://ieeexplore.ieee.org/xpl/articleDetails.jsp?arnumber=7428009}{Stitch aware detailed placement for multiple e-beam lithography}'', 
    IEEE/ACM Asia and South Pacific Design Automation Conference (ASPDAC), Macau, China, Jan 25-28, 2016.
    
}
            

\item[{[C4]}]{
        \textbf{Yibo Lin}, Bei Yu, Biying Xu and David Z. Pan*, 
    ``\href{http://dl.acm.org/citation.cfm?id=2840875}{Triple patterning aware detailed placement toward zero cross-row middle-of-line conflict}'', 
    IEEE/ACM International Conference on Computer-Aided Design (ICCAD), Austin, TX, Nov 2-6, 2015.
    
}
            

\item[{[C3]}]{
        \textbf{Yibo Lin}, Bei Yu and David Z. Pan*, 
    ``\href{http://dl.acm.org/citation.cfm?id=2744769.2744850}{High performance dummy fill insertion with coupling and uniformity constraints}'', 
    ACM/IEEE Design Automation Conference (DAC), San Francisco, CA, Jun 7-11, 2015.
    
}
            

\item[{[C2]}]{
        David Z. Pan*, Lars Liebmann, Bei Yu, Xiaoqing Xu and \textbf{Yibo Lin}, 
    ``\href{http://dl.acm.org/citation.cfm?id=2744769.2747940}{Pushing multiple patterning in sub-10nm: are we ready?}'', 
    ACM/IEEE Design Automation Conference (DAC), San Francisco, CA, Jun 7-11, 2015.
    (\textbf{Invited Paper})
}
            

\item[{[J1]}]{
        Bei Yu, Xiaoqing Xu, Jhih-Rong Gao, \textbf{Yibo Lin}, Zhuo Li, Charles Alpert and David Z. Pan*, 
    ``\href{https://doi.org/10.1109/TCAD.2015.2401571}{Methodology for standard cell compliance and detailed placement for triple patterning lithography}'', 
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), May, 2015.
    
}
            

%}}}
\end{description}
    

\end{rSection}


