\begin{rSection}{10篇代表性论文}

  按时间倒序排列。标*表示通讯作者。

\begin{enumerate}
%{{{

\item{
        Yifan Chen, Zaiwen Wen, Yun Liang and \textbf{Yibo Lin}*, 
    ``\href{https://doi.org/10.1109/ICCAD57390.2023.10323700}{Stronger Mixed-Size Placement Backbone Considering Second-Order Information}'', 
    IEEE/ACM International Conference on Computer-Aided Design (ICCAD), San Francisco, CA, Oct 29-31, 2023.
}
\item{
        Haoyi Zhang, Xiaohan Gao, Haoyang Luo, Jiahao Song, Xiyuan Tang, Junhua Liu, \textbf{Yibo Lin}*, Runsheng Wang and Ru Huang, 
    ``\href{https://doi.org/10.23919/DATE56975.2023.10137296}{SAGERoute: Synergistic Analog Routing Considering Geometric and Electrical Constraints with Manual Design Compatibility}'', 
    IEEE/ACM Proceedings Design, Automation and Test in Europe (DATE), Antwerp, Belgium, Apr 17-19, 2023.
    (\textbf{Best Paper Award})
}
\item{
        Jing Mai, Jiarui Wang, Zhixiong Di and \textbf{Yibo Lin}*, 
    ``\href{https://doi.org/10.1109/TCAD.2023.3313101}{Multi-Electrostatic FPGA Placement Considering SLICEL-SLICEM Heterogeneity, Clock Feasibility, and Timing Optimization}'', 
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), Sep, 2023.
}
\item{
        Zizheng Guo, Tsung-Wei Huang and \textbf{Yibo Lin}*, 
    ``\href{https://doi.org/10.1109/TCAD.2023.3286261}{Accelerating Static Timing Analysis using CPU-GPU Heterogeneous Parallelism}'', 
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), Jun, 2023.
}
\item{
        Qipan Wang, Xiaohan Gao, \textbf{Yibo Lin}*, Runsheng Wang and Ru Huang, 
    ``\href{https://doi.org/10.1145/3508352.3549398}{DeePEB: A Neural Partial Differential Equation Solver for Post Exposure Baking Simulation in Lithography}'', 
    IEEE/ACM International Conference on Computer-Aided Design (ICCAD), San Diego, CA, Nov 01-03, 2022.
    (\textbf{Best Paper Nomination})
}
\item{
        Zizheng Guo and \textbf{Yibo Lin}*, 
    ``\href{https://doi.org/10.1145/3489517.3530486}{Differentiable-Timing-Driven Global Placement}'', 
    ACM/IEEE Design Automation Conference (DAC), San Francisco, CA, Jul 10-14, 2022.
}
\item{
        Siting Liu, Peiyu Liao, Zhitang Chen, Wenlong Lv, \textbf{Yibo Lin}* and Bei Yu*, 
    ``\href{https://doi.org/10.23919/DATE54114.2022.9774606}{FastGR: Global Routing on CPU-GPU with Heterogeneous Task Graph Scheduler}'', 
    IEEE/ACM Proceedings Design, Automation and Test in Europe (DATE), Antwerp, Belgium, Mar 14-23, 2022.
    (\textbf{Best Paper Award})
}
\item{
        Zizheng Guo, Jing Mai and \textbf{Yibo Lin}*, 
    ``\href{https://doi.org/10.1109/DAC18074.2021.9586149}{Ultrafast CPU/GPU Kernels for Density Accumulation in Placement}'', 
    ACM/IEEE Design Automation Conference (DAC), San Francisco, CA, Dec 05-09, 2021.
    
}
\item{
        Zizheng Guo, Tsung-Wei Huang and \textbf{Yibo Lin}*, 
    ``\href{https://doi.org/10.1109/DAC18074.2021.9586085}{A Provably Good and Practically Efficient Algorithm for Common Path Pessimism Removal in Large Designs}'', 
    ACM/IEEE Design Automation Conference (DAC), San Francisco, CA, Dec 05-09, 2021.
    
}
\item{
        \textbf{Yibo Lin}*, Zixuan Jiang, Jiaqi Gu, Wuxi Li, Shounak Dhar, Haoxing Ren, Brucek Khailany and David Z. Pan, 
    ``\href{https://doi.org/10.1109/TCAD.2020.3003843}{DREAMPlace: Deep Learning Toolkit-Enabled GPU Acceleration for Modern VLSI Placement}'', 
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), Apr, 2021.
    (\textbf{Best Paper Award})
}

%}}}
\end{enumerate}

\end{rSection}
