
\begin{rSection}{学术服务}

\textbf{技术程序委员会成员}
\begin{itemize}
    \item ACM/IEEE Design Automation Conference (DAC): 2020.
    \item IEEE/ACM International Conference on Computer-Aided Design (ICCAD): 2018, 2019, 2020, 2021.
    \item IEEE International Conference on Computer Design (ICCD): 2019.
    \item IEEE/ACM Asia and South Pacific Design Automation Conference (ASPDAC): 2021, 2022.
    \item ACM International Symposium on Physical Design (ISPD): 2020.
    \item ACM/IEEE Workshop on Machine Learning for CAD (MLCAD): 2021.
    \item ACM Great Lakes Symposium on VLSI (GLVLSI): 2024.
    \item Workshop on Synthesis And System Integration of Mixed Information technologies (SASIMI): 2021.
    \item IEEE Electron Devices Technology and Manufacturing Conference (EDTM): 2021.
    \item IEEE International Conference on Artificial Intelligence Circuits and Systems (AICAS): 2022. 
\end{itemize}

\textbf{期刊审稿人}
\begin{itemize}
    \item IEEE Transaction on Computer-Aided Design of Integrated Circuits and Systems (TCAD).
    \item IEEE Transactions on Computers (TC).
    \item ACM Transaction on Design Automation of Electronic Systems (TODAES).
    \item SPIE Journal of Micro/Nanolithography, MEMS, and MOEMS (JM3).
    \item Elsevier, Integration, the VLSI Journal (Integration).
\end{itemize}

\textbf{期刊编辑}
\begin{itemize}
    \item ACM Transaction on Design Automation of Electronic Systems (TODAES) Special Issue on MLCAD, 2022.
\end{itemize}

\textbf{执行委员会成员}
\begin{itemize}
    \item ACM/IEEE Workshop on Machine Learning for CAD (MLCAD) 2021, financial chair.
\end{itemize}

\end{rSection}


